### 2024-08-09 paper/main.tex
fix img path & add paper outline

\documentclass[a4paper]{article}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{natbib}

\usepackage[margin=1.25in]{geometry}
\usepackage{hyperref} % links
\usepackage{parskip} % proper paragraphs, no indentation
\usepackage{pdfpages} % add non-plagiarism statement

% For showing the month + year only as the date:
\usepackage[en-GB]{datetime2}
\DTMlangsetup{showdayofmonth=false}

\usepackage{xcolor}
\usepackage{blindtext} % for adding the "lorem ipsum" filler sections. delete this once you start writing your thesis.

\usepackage{graphicx}
\graphicspath{{./images/}}
\usepackage{float}

% This is used in the PDF meta data
\title{SBAT: A Simple Browser-based Annotation Tool}
\author{Jia Sheng}
\date{\today}

\begin{document}

% The actual title page of your thesis:
\begin{titlepage}
\begin{center}

\hrule
\vspace{0.6cm}
{\bfseries\huge
SBAT: A Simple Browser-based Annotation Tool
}\\[1cm] 
\hrule
\vspace*{.05\textheight}

\begin{minipage}[t]{0.49\textwidth}
\begin{flushleft} 
{\large
\textit{Author}\\
Jia Sheng}\\
\href{mailto:jia.sheng@student.uni-tuebingen.de}{\textit{jia.sheng@student.uni-tuebingen.de}}\\
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.49\textwidth}
\begin{flushright}
{\large
\textit{Supervisor}\\
Çagri Çöltekin}\\
\href{mailto:ccoltekin@sfs.uni-tuebingen.de}{\textit{ccoltekin@sfs.uni-tuebingen.de}}\\
\end{flushright}
\end{minipage}\\

\vfill

\vspace*{.1\textheight}

{\large Seminar für Sprachwissenschaft\\
Eberhard Karls Universität Tübingen

\vspace{1em}
\today}
\end{center}
\end{titlepage}

% No page numbering for the abstract, the anti-plagiarism statement and the table of contents.
\pagenumbering{gobble}

%% Uncomment once you want to add the anti-plagiarism statement file
% \newpage
% \includepdf[pages=-]{name-of-anti-plagiarism-statement-file}

\newpage
%\tableofcontents
%\listoftables
%\listoffigures
\newpage

\pagenumbering{arabic}

\section{Introduction}
\begin{enumerate}
\item Reason to make this tool: \\
large annotation projects involve many annotators\\
a centrally managed tool needed\\
\item limitation of current annotation tool:\\ 
needs to be hosted on a server\\
offline version needs installation\\
\item introduce SBAT, a browser-based tool for text annotation, can be combined well with github
\end{enumerate}
\section{Related Work}
\begin{enumerate}
\item brat
\item brat-frontend-editor
\item sbat old version by Charlotte
\end{enumerate}
\section{Features}
\begin{enumerate}
\item High-quality Annotation Visualisation and intuitive annotation interface from Brat
\item web interface, no need to register
\item import and export annotations through ui from github
\end{enumerate}
\section{Implementation}
\begin{enumerate}
\item annotation ui from brat
\item static web app hosted on github pages, no need of server
\item github API for reading and writing annotation files
\end{enumerate}

\section{Conclusion}
SBAT, a light-weight and easy-to-use tool for text annotation projects.\\ 
Annotation UI based on Brat, but made completely online, and enables user to import from / export to their own github repo.

%\begin{figure}[H]
%\centering
%\includegraphics[scale=0.2]{rag.png}
%\caption{Retrieval Augmented Generation}
%Source: https://techcommunity.microsoft.com/t5/azure-ai-services-blog/revolutionize-your-enterprise-data-with-chatgpt-next-gen-apps-w/ba-p/3762087
%\end{figure}

%\begin{figure}[H]
%\centering
%\includegraphics[scale=0.6]{flow_chart.png}
%\caption{Flow chart}
%\end{figure}

%\begin{enumerate}
%\item 
%\item 
%\item 
%\end{enumerate}

%\bibliography{bibliography}
%\bibliographystyle{chicago}

\end{document}

### 2024-08-17 paper/main.tex
add option button & update paper outline

@@
 % This is used in the PDF meta data
-\title{SBAT: A Simple Browser-based Annotation Tool}
+\title{SBAT: A Simple Browser-based Annotation Tool with Interactive UI and Github Support}
 \author{Jia Sheng}
@@
 \vspace{0.6cm}
-{\bfseries\huge
-SBAT: A Simple Browser-based Annotation Tool
+{\bfseries\LARGE
+SBAT: A Simple Browser-based Annotation Tool with Interative UI and Github Support
 }\\[1cm]
@@
 \section{Introduction}
+This paper introduces a SBAT, a light-weighted and easy-to-use web annotation tool.
+Although there are already various apps developed for the purpose of text annotation, they often required to be hosted on a server, which increases the threshold of usage.
+In comparison, SBAT is developed to be used in a web UI without need of registration or a dedicated server, while still keeping the necessary functions of the heavier annotation tools.
 \begin{enumerate}
-\item Reason to make this tool: \\
+\item 
+Motivation: \\
+Easy to use for smaller projects, no budget for a server\\
 large annotation projects involve many annotators\\
@@
 offline version needs installation\\
+heavy\\
 \item introduce SBAT, a browser-based tool for text annotation, can be combined well with github
@@
 \item sbat old version by Charlotte
+\item ud-annotatrix
+\item inception
 \end{enumerate}
@@
 \item annotation ui from brat
-\item static web app hosted on github pages, no need of server
+\item static web app hosted on github pages, no need of server, no server-side configuration, light-weighted
 \item github API for reading and writing annotation files

### 2024-08-17 client/src/Brat.js

@@ -49,6 +49,102 @@ export class BratFrontendEditor {
             <div id="commentpopup"></div>
             <div id="svg"></div>
 
+            <!-- Options dialog -->
+            <form id="options_form" class="dialog" title="Options">
+            <fieldset id="options_form_visual">
+                <legend>Visual options</legend>
+                <div class="optionRow">
+                    <span class="optionLabel">Abbreviate labels</span>
+                    <span id="label_abbreviations" class="radio_group small-buttons">
+                        <input type="radio" id="label_abbreviations_off" value="off" name="label_abbrev_radio" />
+                        <label for="label_abbreviations_off" title="Always display full form of labels.">Off</label>
+                        <input type="radio" id="label_abbreviations_on" value="on" name="label_abbrev_radio"
+                            checked="checked" />
+                        <label for="label_abbreviations_on"
+                            title="Abbreviate annotation labels in limited space.">On</label>
+                    </span>
+                </div>
+                <div class="optionRow">
+                    <span class="optionLabel">Text background</span>
+                    <span id="text_backgrounds" class="radio_group small-buttons">
+                        <input type="radio" id="text_backgrounds_blank" value="blank" name="text_background_radio" />
+                        <label for="text_backgrounds_blank" title="Blank white text backgrounds.">Blank</label>
+                        <input type="radio" id="text_backgrounds_striped" value="striped" name="text_background_radio"
+                            checked="checked" />
+                        <label for="text_backgrounds_striped"
+                            title="Striped text backgrounds with every second sentence on light gray background.">Striped</label>
+                    </span>
+                </div>
+                <div class="optionRow">
+                    <span class="optionLabel">Layout density</span>
+                    <span id="layout_density" class="radio_group small-buttons">
+                        <input type="radio" id="layout_density1" value="1" name="layout_radio" />
+                        <label for="layout_density1"
+                            title="Dense annotation layout: minimizes space taken by annotations.">Dense</label>
+                        <input type="radio" id="layout_density2" value="2" name="layout_radio" checked="checked" />
+                        <label for="layout_density2"
+                            title="Normal annotation layout density: balances between annotation size and readability.">Normal</label>
+                        <input type="radio" id="layout_density3" value="3" name="layout_radio" />
+                        <label for="layout_density3"
+                            title="Spacious annotation layout: allows extra space for annotations to improve readability.">Spacious</label>
+                    </span>
[…]

### 2024-08-17 index.js

@@ -320,6 +320,40 @@ async function pushCommit() {
 
 showDocButton.addEventListener('click', () => console.log(docData));
 
+/*
+var optionsForm = $('#options_form');
+var optionsFormSubmit = function (evt) {
+    dispatcher.post('hideForm');
+    return false;
+};
+optionsForm.submit(optionsFormSubmit);
+initForm(optionsForm, {
+    width: 550,
+    resizable: false,
+    no_cancel: true,
+    open: function (evt) {
+        keymap = {};
+    }
+});
+$('#options_button').click(function () {
+    dispatcher.post('showForm', [optionsForm]);
+});
+// make nice-looking buttons for checkboxes and radios
+$('#options_form').find('input[type="checkbox"]').button();
+$('#options_form').find('.radio_group').buttonset();
+$('#rapid_model').addClass('ui-widget ui-state-default ui-button-text');
+
+var fillDisambiguatorOptions = function (disambiguators) {
+    $('#annotation_speed3').button(disambiguators.length ? 'enable' : 'disable');
+    //XXX: We need to disable rapid in the conf too if it is not available
+    var $rapid_mode = $('#rapid_model').html('');
+    $.each(disambiguators, function (modelNo, model) {
+        var $option = $('<option/>').attr('value', model[2]).text(model[2]);
+        $rapid_mode.append($option);
+    });
+};
+*/
+
 /* Implementation of uploading and downloading local file:
 
             <div id="downloadArea" class="block">

### 2024-08-28 paper/main.tex
update paper

@@
 % This is used in the PDF meta data
-\title{SBAT: A Simple Browser-based Annotation Tool with Interactive UI and Github Support}
+\title{SBAT: A Simple Browser-based Annotation Tool with Interactive Visualization and Github Support}
 \author{Jia Sheng}
@@
 
+A thesis submitted in partial fulfilment\\
+of the requirements for the degree of\\[2mm]
+{\large Bachelor of Arts}\\
+in\\[1mm]
+{\large International Studies in Computational Linguistics}
+
 \vspace*{.1\textheight}
@@
 \newpage
-%\tableofcontents
+\tableofcontents
 %\listoftables
@@
 This paper introduces a SBAT, a light-weighted and easy-to-use web annotation tool.
-Although there are already various apps developed for the purpose of text annotation, they often required to be hosted on a server, which increases the threshold of usage.
-In comparison, SBAT is developed to be used in a web UI without need of registration or a dedicated server, while still keeping the necessary functions of the heavier annotation tools.
-\begin{enumerate}
-\item 
-Motivation: \\
-Easy to use for smaller projects, no budget for a server\\
-large annotation projects involve many annotators\\
-a centrally managed tool needed\\
-\item limitation of current annotation tool:\\ 
-needs to be hosted on a server\\
-offline version needs installation\\
-heavy\\
-\item introduce SBAT, a browser-based tool for text annotation, can be combined well with github
-\end{enumerate}
+It supports text annotation tasks that require attachment of labels, such as POS tagging or labeling for named entity recognition.
+There have been various apps developed for the purpose of linguistic annotation, but they often require a dedicated server or a local installation, which complicates the usage.
+Basing on the annotation interface of Brat, SBAT is developed for easier start of text annotation while retaining the most essential functions.
+It is completely browser-based, without the need of any server, and can be well combined with Github's file management function.
+
 \section{Related Work}
+Among the annotation tools, Brat is a powerful scheme-neutral annotation tool with intuitive and user-friendly interfaces.
+\cite{stenetorp-etal-2012-brat} It can be used for tasks including but not limited to POS tagging, named entity recognition, semantic role labeling, dependancy and verb frame annotations, and enables user-defined contraints-checking.
+Besides, it provides a high-quality visualization of annotations by its browser-based UI component implemented in XHTML, Scalable Vector Graphics (SVG) and JavaScript.
+However, a CGI-capable server is required by the installation, which combines all user modifications real-time with the stored data.
+This is the main difference in brat-frontend-editor, a forked project of the original Brat.
+\cite{brat-frontend-editor}
 \begin{enumerate}
 \item brat
+There have been various of tools developed for text annotation in linguistics field.
+Among them, Brat is a scheme-neutral web-based annotation tool with intuitive and user-friendly interfaces and NLP technology.
+Its vector graphics-based component enables high-quality visualisation, It supports most text annotation tasks including but not limited to POS tagging, named entity recognition, semantic role labeling, dependancy and verb frame annotations, and allows user-defined contraints checking for annotations.
+Moreover, it integrated a ML-based semantic class disambiguations system that offers multiple outputs with probability estimates, which was proven to increase annotator productivity.
+It includes a client user interface implemented by XHTML and Scalable Vector Graphics (SVG) and a backend server implemented in Python.
+Its insllation requires a CGI-capable web server.
+JavaScript and XML (Ajax) was used for the asynchronous communication between client and server.
 \item brat-frontend-editor
+SBAT frontend UI also refers to "brat-frontend-editor", a forked project of Brat.
+It is a standalone version of the brat annotator frontend without the need of server-side code, rewriting all client-server communications to pure browser executions.
 \item sbat old version by Charlotte
+This is the previous version of SBAT, with the goal to create an annotation UI based on browser without need of a server.
+This web page was realized using JavaScript and HTML, and allows annotation of paragraphs, which can be used for, e.g.
+sentiment analysis.
 \item ud-annotatrix
+A tool designed specifically for annotations of Universal Dependencies.
+It accepts several input formats including plain text and CoNNL-U, and offers user the Graphical editing function.
+Unlike Brat, it offers a stand-alone module, which is written in JavaScript with locally saved dependencies and stores imported corpora in localStorage, allowing offline usage.
+One can also use the server module to save corpora on server.
 \item inception
+INCEpTION is another software designed for specific annotation tasks, in this case for semantic annotation.
+It is a modular annotation platform that widely adopts machine learning to enable recommenders to provide annotation suggestions as well as active learning mode which learns from the feedback of the user to further improve suggestions quality.
+It shows the tendancy of more field-specificity and machine-assistance in the development of annotation tools.
+A software for semantic annotation.
+Recommenders: algorithms that make use of machine learning and/or internal knowledge bases to provide annotation suggestions, to provide users with suggestions for possible labels, active learning mode: solicite feedback from the user, to quickly reach a good quality of annotation suggestions, to guide the annotator.
+Gives suggestions at any time during the annotation process and learns from user interactions.supports rdf-based knowledge bases for knowledge management.
 \end{enumerate}
@@
 \begin{enumerate}
-\item High-quality Annotation Visualisation and intuitive annotation interface from Brat
+\item Interactive Annotation Interface
+The annotation interface of SBAT is completely based on that of BRAT, which is interactive, intuitive and easy-to-use.
+To add an annotation, one can simply double-click a word or select a span with the mouse, and then select the labels in the pop-up window.
+The size and display of the interface can be adjusted by the option button, and the labels and their corresponding color can be defined in the JSON config file.
 \item web interface, no need to register
-\item import and export annotations through ui from github
+SBAT is browser-based, which means one can simply open the website and start annotating in the browser.
+But unlike Brat, all logics of SBAT are completely executed in the browser, so there is no need to configure a server or install any other software.
+\item import and export annotations through ui from github.
+Another advantage of SBAT is its support for github.
+The user only has to enter his own Github Personal Access Token, and can then import files to annotate from his github repositories and export his annotations by making a commit in the same repository.
+By making use of github commit, the versions of annotations can be well documented and managed.
+The annotations are exported to a JSON file with attributes like text, tokens, entites....
+For file import, all file types are supported, but only annotations in JSON file with these specific attributes can be visualized in the annotation interface, other file types will be simply treated as txt file, i.e.
+the complete content will be displayed as pure text which can be annotated.
+\item potential for collaboration in annotation project
+The usage of github repositories to store annotations also enables colloboration and project management.
+There is a admin config attribute in the JSON config file, which can be modified by the admin to specify the common repository to work on.
+Then, by sharing the repository to all team members, a team will be able to work on the same annotation project.
+Different branches can also be created for different members to create and compare multiple versions of annotations.
 \end{enumerate}
@@
 \item annotation ui from brat
+The annotation user interface is made with the frontend UI component from Brat, which is implemented using XHTML, Scalable Vector Graphics (SVG), JavaScript, and jQuery.
+Moreover, to get rid of the dependancy on a server, all user actions such as creating, editing or deleting annotations are handled by the browser.
+This is realized by the LocalAjax class, which is written based on the LocalAjax function in brat-frontend-editor and is a local simulation of AJAX requests processing the data without actually sending real network requests.
+Other UI elements, such as the login buttons, are also implemented using HTML and Asynchronous JavaScript.
 \item static web app hosted on github pages, no need of server, no server-side configuration, light-weighted
+SBAT is a static web app that is hosted on github pages, and as there is no need of a server or any server-side configuration, anyone who have downloaded the repository can simply change the configurations and then host it on their own github pages.
+If it is not an annotation project which requires collaboration of many members, SBAT can also simply be used locally, by starting the index.js file in the local browser.
 \item github API for reading and writing annotation files
+SBAT uses Octokit, the official SDKs for the Github API.
+octokit.js v4.0.2 [Computer software]. (2024). Retrieved from https://github.com/octokit/octokit.js
+The user authentication through Github Personal Access Token enables creating a new user-authenticated Octokit object and obtaining information about branches and file content from the configured repository.
+Likewise, creating a new commit and pushing to github repository is realized by first obtaining tree of all files from last commit, modifying the changed file or creating a new file, and the creating the new tree and commit with the octokit REST API endpoint.
 \end{enumerate}
@@
 \section{Conclusion}
-SBAT, a light-weight and easy-to-use tool for text annotation projects.\\ 
-Annotation UI based on Brat, but made completely online, and enables user to import from / export to their own github repo.
+SBAT is an annotation tool that can be used to attach annotation labels to linguistic data.
+It is completely browser-based and only requires a browser to be executed.
+Furthermore, it can be combined well with github to import from and export annotations to user's own github repositories.
+It aims to provide a more simplified and no-server solution for annotation projects.\\
 
@@
 
-%\bibliography{bibliography}
-%\bibliographystyle{chicago}
+\bibliography{bibliography}
+\bibliographystyle{plain}
 

### 2024-08-29 paper/main.tex
update related work

@@
 {\bfseries\LARGE
-SBAT: A Simple Browser-based Annotation Tool with Interative UI and Github Support
+SBAT: A Simple Browser-based Annotation Tool with Interative Visualization and Github Support
 }\\[1cm]
@@
 \section{Related Work}
-Among the annotation tools, Brat is a powerful scheme-neutral annotation tool with intuitive and user-friendly interfaces.
-\cite{stenetorp-etal-2012-brat} It can be used for tasks including but not limited to POS tagging, named entity recognition, semantic role labeling, dependancy and verb frame annotations, and enables user-defined contraints-checking.
+Among the annotation tools, Brat \cite{stenetorp-etal-2012-brat} is a powerful scheme-neutral annotation tool with intuitive and user-friendly interfaces.
+And it is extremely important for this paper as SBAT is developed upon its UI component.
+Brat can be used for tasks including but not limited to POS tagging, named entity recognition, semantic role labeling, dependancy and verb frame annotations, and enables user-defined contraints-checking.
 Besides, it provides a high-quality visualization of annotations by its browser-based UI component implemented in XHTML, Scalable Vector Graphics (SVG) and JavaScript.
-However, a CGI-capable server is required by the installation, which combines all user modifications real-time with the stored data.
-This is the main difference in brat-frontend-editor, a forked project of the original Brat.
-\cite{brat-frontend-editor}
-\begin{enumerate}
-\item brat
-There have been various of tools developed for text annotation in linguistics field.
-Among them, Brat is a scheme-neutral web-based annotation tool with intuitive and user-friendly interfaces and NLP technology.
-Its vector graphics-based component enables high-quality visualisation, It supports most text annotation tasks including but not limited to POS tagging, named entity recognition, semantic role labeling, dependancy and verb frame annotations, and allows user-defined contraints checking for annotations.
-Moreover, it integrated a ML-based semantic class disambiguations system that offers multiple outputs with probability estimates, which was proven to increase annotator productivity.
-It includes a client user interface implemented by XHTML and Scalable Vector Graphics (SVG) and a backend server implemented in Python.
-Its insllation requires a CGI-capable web server.
-JavaScript and XML (Ajax) was used for the asynchronous communication between client and server.
-\item brat-frontend-editor
-SBAT frontend UI also refers to "brat-frontend-editor", a forked project of Brat.
-It is a standalone version of the brat annotator frontend without the need of server-side code, rewriting all client-server communications to pure browser executions.
-\item sbat old version by Charlotte
-This is the previous version of SBAT, with the goal to create an annotation UI based on browser without need of a server.
-This web page was realized using JavaScript and HTML, and allows annotation of paragraphs, which can be used for, e.g.
-sentiment analysis.
-\item ud-annotatrix
-A tool designed specifically for annotations of Universal Dependencies.
-It accepts several input formats including plain text and CoNNL-U, and offers user the Graphical editing function.
+Last but not the least, Brat integrats a ML-based semantic class disambiguator that outputs multiple annotations with their posibility estimates, which was proven to increase the efficiency of annotators.\\
+\\
+Although Brat is a very capable annotation tool, it is not necessarily the simpliest to use.
+A CGI-capable server is required by its installation, which will combine all user modifications real-time with the stored data.
+That is where brat-frontend-editor, a forked project of Brat, differentiates itself with the original project.
+Brat-frontend-editor \cite{brat-frontend-editor} is a standalone browser version of Brat that do not require a server.
+This project is since 2018 no longer maintained, however, its transformation of server-side operations into browser-only operations serves as important reference in the development of SBAT.\\
+\\
+While Brat serves as a general-purpose annotation tool, more recent tools target at more specific annotation schemes.
+UD Annotatrix \cite{tyers-etal-2017-ud}, for example, is specifically designed for annotations of universal dependencies.
+It accepts several input formats including plain text and CoNNL-U, and offers user Graphical editing function.
 Unlike Brat, it offers a stand-alone module, which is written in JavaScript with locally saved dependencies and stores imported corpora in localStorage, allowing offline usage.
-One can also use the server module to save corpora on server.
-\item inception
-INCEpTION is another software designed for specific annotation tasks, in this case for semantic annotation.
-It is a modular annotation platform that widely adopts machine learning to enable recommenders to provide annotation suggestions as well as active learning mode which learns from the feedback of the user to further improve suggestions quality.
-It shows the tendancy of more field-specificity and machine-assistance in the development of annotation tools.
-A software for semantic annotation.
-Recommenders: algorithms that make use of machine learning and/or internal knowledge bases to provide annotation suggestions, to provide users with suggestions for possible labels, active learning mode: solicite feedback from the user, to quickly reach a good quality of annotation suggestions, to guide the annotator.
-Gives suggestions at any time during the annotation process and learns from user interactions.supports rdf-based knowledge bases for knowledge management.
-\end{enumerate}
+But there is also a server module to save corpora on server.\\
+\\
+Another specific-purpose annotation tool is INCEpTION \cite{klie-etal-2018-inception}, which is used for semantic annotation.
+What differentiates it from the previously-introduced tools is its wide adoption of machine learning models to assist annotation process.
+It not only utilizes recommenders based on machine learning models to provide users with suggestions for possible labels, but also has an active learning mode where user's feedback can be used to further improve the quality of those suggestions.
+It also has a comprehensive user management system, where admin can create multiple user accounts for the project and assign them different roles.
+In terms of the software itself, INCEpTION is a Java application with Spring Boot backend and a web user interface, so its usage requires installation of Java as well as the software.\\
+\\
+Lastly, the initial version of SBAT \cite{SBAT} serves as one of the basis of the current SBAT version.
+The development of this previous version has the same goal, which is to achieve a simple but functional annotation tool that is completely browser-based, without any server-side configuration.
+It is implemented using HTML and JavaScript, and can be used to define and attach labels to paragraphs, as well as import and export annotation files.
 \section{Features}

### 2024-08-31 paper/main.tex
update features

@@
 \section{Related Work}
-Among the annotation tools, Brat \cite{stenetorp-etal-2012-brat} is a powerful scheme-neutral annotation tool with intuitive and user-friendly interfaces.
+Among the annotation tools, Brat \cite{stenetorp-etal-2012-brat} is a powerful scheme-neutral annotation tool with intuitive and user-friendly interface.
 And it is extremely important for this paper as SBAT is developed upon its UI component.
@@
 \\
-Another specific-purpose annotation tool is INCEpTION \cite{klie-etal-2018-inception}, which is used for semantic annotation.
+Another specialized annotation tool is INCEpTION \cite{klie-etal-2018-inception}, which is used for semantic annotation.
 What differentiates it from the previously-introduced tools is its wide adoption of machine learning models to assist annotation process.
@@
 \section{Features}
-\begin{enumerate}
-\item Interactive Annotation Interface
-The annotation interface of SBAT is completely based on that of BRAT, which is interactive, intuitive and easy-to-use.
-To add an annotation, one can simply double-click a word or select a span with the mouse, and then select the labels in the pop-up window.
-The size and display of the interface can be adjusted by the option button, and the labels and their corresponding color can be defined in the JSON config file.
-\item web interface, no need to register
+\subsection{Interactive User Interface}
+Based on Brat, the annotation UI of SBAT is responsive, interactive and intuitive to use.
+To add an annotation, one can simply double-click or select a span with his mouse, and then select corresponding label in the pop-up window.
+All added labels will be visualized with tags above the annotated text, and different tags differentiate with each other by the user-defined color.
+And if the user has added comments, they will be shown with a mouse hover.
+The size and display of the interface can be adjusted by the option button, and the labels and their style are defined in the JSON config file.
+Besides the main component for annotating text, there is also a step-by-step guide in the beginning for github authentication as well as the export function, all with clear instructions.
+\subsection{Browser-Based Application}
 SBAT is browser-based, which means one can simply open the website and start annotating in the browser.
-But unlike Brat, all logics of SBAT are completely executed in the browser, so there is no need to configure a server or install any other software.
-\item import and export annotations through ui from github.
-Another advantage of SBAT is its support for github.
-The user only has to enter his own Github Personal Access Token, and can then import files to annotate from his github repositories and export his annotations by making a commit in the same repository.
-By making use of github commit, the versions of annotations can be well documented and managed.
-The annotations are exported to a JSON file with attributes like text, tokens, entites....
-For file import, all file types are supported, but only annotations in JSON file with these specific attributes can be visualized in the annotation interface, other file types will be simply treated as txt file, i.e.
-the complete content will be displayed as pure text which can be annotated.
-\item potential for collaboration in annotation project
-The usage of github repositories to store annotations also enables colloboration and project management.
-There is a admin config attribute in the JSON config file, which can be modified by the admin to specify the common repository to work on.
-Then, by sharing the repository to all team members, a team will be able to work on the same annotation project.
-Different branches can also be created for different members to create and compare multiple versions of annotations.
-\end{enumerate}
+But unlike Brat, all logics of SBAT are completely executed in the browser, there is no need of software installation or server configuration.
+One can either store its front-end files in a Github repository to access it via Github pages online, or download the those files to start it locally in the browser.
+Due to its simple structure, it is fast to run and easy to adapt for different purposes.
+\subsection{Github Support}
+SBAT can not only be hosted on Github Pages, but also supports import files from or export annotations to Github repositories.
+To do so, the user only has to enter his Github Personal Access Token (information about the repository name as well as the its owner's user name are entered in advance under "admin config" in the JSON config file), and can then select the github branch as well as the file to open.
+For importing file, all file formats are supported, and they will be treated as txt file, i.e.
+the whole content will be displayed as annotation-ready text in the interface.
+The only exception is JSON file which has been previously exported from SBAT (which has attributes like text, tokens, entities...) -- Their content will be parsed and the annotations saved in the file will be visualized.
+To export annotations, the user can optionally leave a commit message and click the "commit" button, a JSON file with original texts and annotations will be commited to the same Github repository from which the file was originally imported.
+By making use of Github commit, the versions of annotations can be well documented and managed.
+\subsection{Project Management Support}
+SBAT's support for Github also provides possibility for user management in annotation projects.
+For instance, the admin can create a Github repository for an annotation project and add the repository and owner information in SBAT's config file.
+By sharing access to this repository with different users, they can contribute to the same project at the same time.
+Moreover, different branches can be created for different users to create and compare multiple versions.
+This utilization of Github's file management system facilitates the colloboration of multiple annotators in an annotation project.
 \section{Implementation}

### 2024-09-01 paper/main.tex
update implementation

@@
 \section{Implementation}
-\begin{enumerate}
-\item annotation ui from brat
-The annotation user interface is made with the frontend UI component from Brat, which is implemented using XHTML, Scalable Vector Graphics (SVG), JavaScript, and jQuery.
-Moreover, to get rid of the dependancy on a server, all user actions such as creating, editing or deleting annotations are handled by the browser.
-This is realized by the LocalAjax class, which is written based on the LocalAjax function in brat-frontend-editor and is a local simulation of AJAX requests processing the data without actually sending real network requests.
-Other UI elements, such as the login buttons, are also implemented using HTML and Asynchronous JavaScript.
-\item static web app hosted on github pages, no need of server, no server-side configuration, light-weighted
-SBAT is a static web app that is hosted on github pages, and as there is no need of a server or any server-side configuration, anyone who have downloaded the repository can simply change the configurations and then host it on their own github pages.
-If it is not an annotation project which requires collaboration of many members, SBAT can also simply be used locally, by starting the index.js file in the local browser.
-\item github API for reading and writing annotation files
-SBAT uses Octokit, the official SDKs for the Github API.
-octokit.js v4.0.2 [Computer software]. (2024). Retrieved from https://github.com/octokit/octokit.js
+\subsection{Annotation Interface}
+SBAT's annotation interface is rooted in the frontend component from Brat, which is implemented using XHTML, Scalable Vector Graphics (SVG), JavaScript, and jQuery.
+On top of that, to remove the dependance on a server, all user actions such as creating, editing or deleting annotations are handled by the browser.
+This is realized by the LocalAjax class, adapting the LocalAjax function from brat-frontend-editor.
+It locally simulates AJAX requests to process the data without actually sending real network requests.
+Other UI elements, such as the login buttons, are also created by HTML and Asynchronous JavaScript.
+In this way, the complete user interface is embedded in a HTML webpage and all functions are locally executed in the browser.
+\subsection{Browser-Based Construction}
+As SBAT is a static web app without server communications, it can be hosted on Github Pages for free.
+But it is not mandatory to host the app in order to use it, as the index.js file can be used as an entry point to start the app locally in the browser.
+If the users want to access it online instead of locally, the source code can be directly uploaded to a Github repository to host a copy of SBAT on Github Pages.
+Moreover, to cater to different use cases, it is also easy to modify any part of the app -- SBAT uses ECMAScript Modules instead of CommonJS, so all modules are natively loaded in browser and no module bundler such as webpack is used.
+This allows direct modification of individual modules without the need of re-bundling.
+\subsection{Usage of Github API}
+SBAT uses Octokit \cite{octokit.js}, the official SDKs for the Github API, which enables the programmatical implementation of Github operations.
 The user authentication through Github Personal Access Token enables creating a new user-authenticated Octokit object and obtaining information about branches and file content from the configured repository.
-Likewise, creating a new commit and pushing to github repository is realized by first obtaining tree of all files from last commit, modifying the changed file or creating a new file, and the creating the new tree and commit with the octokit REST API endpoint.
-\end{enumerate}
+Likewise, creating a new commit and pushing to github repository is realized by first obtaining tree of all files from last commit, modifying the changed file or creating a new file, and the creating the new tree and commit it with the REST API endpoint of octokit.
 
 \section{Conclusion}
-SBAT is an annotation tool that can be used to attach annotation labels to linguistic data.
+SBAT is an annotation tool that can be used to attach labels to linguistic data.
 It is completely browser-based and only requires a browser to be executed.
 Furthermore, it can be combined well with github to import from and export annotations to user's own github repositories.
-It aims to provide a more simplified and no-server solution for annotation projects.\\
+It aims to provide a simpler and no-server solution for annotation projects.\\
 

### 2024-09-04 paper/main.tex
update relevant work

@@
-\documentclass[a4paper]{article}
+\documentclass[12ptm a4paper]{article}
 \usepackage[T1]{fontenc}
@@
 
+\linespread{1.5}
+
 % This is used in the PDF meta data
@@
 {\bfseries\LARGE
-SBAT: A Simple Browser-based Annotation Tool with Interative Visualization and Github Support
+SBAT: A Simple Browser-Based Annotation Tool with Interative Visualization and Github Support
 }\\[1cm]
@@
 \newpage
-
 \pagenumbering{arabic}
@@
 \section{Introduction}
-This paper introduces a SBAT, a light-weighted and easy-to-use web annotation tool.
-It supports text annotation tasks that require attachment of labels, such as POS tagging or labeling for named entity recognition.
-There have been various apps developed for the purpose of linguistic annotation, but they often require a dedicated server or a local installation, which complicates the usage.
-Basing on the annotation interface of Brat, SBAT is developed for easier start of text annotation while retaining the most essential functions.
-It is completely browser-based, without the need of any server, and can be well combined with Github's file management function.
+This paper introduces SBAT, a lightweight and easy-to-use web annotation tool.
+It supports annotation tasks that require attaching labels to text data, such as POS tagging or labeling for named entity recognition.
+Various apps have been developed for the purpose of text annotation, but they often require a dedicated server or a local installation, which complicates the usage.
+Therefore, SBAT is designed to be an online annotation tool that is easy to access and simple to use.
+It is built on the Brat annotation interface, but is completely browser-based and server-free, while preserving most of the key functionalities.
+Additionally, it includes support for integration with Github's file management system.
 
 \section{Related Work}
-Among the annotation tools, Brat \cite{stenetorp-etal-2012-brat} is a powerful scheme-neutral annotation tool with intuitive and user-friendly interface.
-And it is extremely important for this paper as SBAT is developed upon its UI component.
-Brat can be used for tasks including but not limited to POS tagging, named entity recognition, semantic role labeling, dependancy and verb frame annotations, and enables user-defined contraints-checking.
-Besides, it provides a high-quality visualization of annotations by its browser-based UI component implemented in XHTML, Scalable Vector Graphics (SVG) and JavaScript.
-Last but not the least, Brat integrats a ML-based semantic class disambiguator that outputs multiple annotations with their posibility estimates, which was proven to increase the efficiency of annotators.\\
+Among the annotation tools, Brat \cite{stenetorp-etal-2012-brat} is a powerful scheme-neutral annotation tool with an intuitive user interface.
+Brat can be used for tasks including but not limited to POS tagging, named entity recognition, semantic role labeling, dependency and verb-frame annotations, and enables user-defined constraints-checking.
+It provides a high-quality visualization of annotations by its browser-based UI component implemented in XHTML, Scalable Vector Graphics (SVG) and JavaScript.
+Last but not least, Brat integrats a ML-based semantic class disambiguator that outputs multiple annotations with their possibility estimates, which has been proven to increase the efficiency of annotators in several annotation projects.\\
 \\
-Although Brat is a very capable annotation tool, it is not necessarily the simpliest to use.
-A CGI-capable server is required by its installation, which will combine all user modifications real-time with the stored data.
-That is where brat-frontend-editor, a forked project of Brat, differentiates itself with the original project.
-Brat-frontend-editor \cite{brat-frontend-editor} is a standalone browser version of Brat that do not require a server.
-This project is since 2018 no longer maintained, however, its transformation of server-side operations into browser-only operations serves as important reference in the development of SBAT.\\
+Despite the success of Brat, it is not the simplest tool to start using.
+A CGI-capable server is required by its installation, in order to combine all user modifications in real-time with the stored data.
+That is where brat-frontend-editor \cite{brat-frontend-editor}, a forked project of Brat, differentiates itself from the original project.
+Brat-frontend-editor is a standalone browser version of Brat that keeps some of its essential editing functions but removes its server-side code.
+It can be imported as a module in vanilla JavaScript, Angular or React.
+This project is since 2018 no longer maintained, so many dependencies have broken, and it no longer keeps up with the new updates of the original Brat.
+However, its transformation of server-side operations into browser-side operations serves as an important reference in the development of SBAT.\\
 \\
-While Brat serves as a general-purpose annotation tool, more recent tools target at more specific annotation schemes.
+While Brat serves as a general-purpose annotation tool, more recent tools target specific annotation schemes.
 UD Annotatrix \cite{tyers-etal-2017-ud}, for example, is specifically designed for annotations of universal dependencies.
-It accepts several input formats including plain text and CoNNL-U, and offers user Graphical editing function.
-Unlike Brat, it offers a stand-alone module, which is written in JavaScript with locally saved dependencies and stores imported corpora in localStorage, allowing offline usage.
-But there is also a server module to save corpora on server.\\
+It accepts several input formats including plain text and CoNNL-U, and offers graphical editing functions.
+Unlike Brat, it offers a stand-alone module written in JavaScript with locally saved dependencies, which stores imported corpora in localStorage and allows offline usage.
+Otherwise, there is also a server module to save corpora on the server.\\
 \\
 Another specialized annotation tool is INCEpTION \cite{klie-etal-2018-inception}, which is used for semantic annotation.
-What differentiates it from the previously-introduced tools is its wide adoption of machine learning models to assist annotation process.
-It not only utilizes recommenders based on machine learning models to provide users with suggestions for possible labels, but also has an active learning mode where user's feedback can be used to further improve the quality of those suggestions.
-It also has a comprehensive user management system, where admin can create multiple user accounts for the project and assign them different roles.
-In terms of the software itself, INCEpTION is a Java application with Spring Boot backend and a web user interface, so its usage requires installation of Java as well as the software.\\
+One of its characteristics is the extensive adoption of machine-learning models to assist the annotation process.
+It not only utilizes recommenders based on machine learning models to provide users with suggestions for possible labels, but also provides an active learning mode where user feedback can be used to further improve the quality of those suggestions.
+It also has a comprehensive user management system, where the admin can create multiple user accounts for the project and assign them different roles.
+In terms of the software itself, INCEpTION is a Java application with Spring Boot backend and a web user interface, so its usage requires the installation of Java as well as the software.\\
 \\
-Lastly, the initial version of SBAT \cite{SBAT} serves as one of the basis of the current SBAT version.
-The development of this previous version has the same goal, which is to achieve a simple but functional annotation tool that is completely browser-based, without any server-side configuration.
-It is implemented using HTML and JavaScript, and can be used to define and attach labels to paragraphs, as well as import and export annotation files.
+Lastly, the previous version of SBAT \cite{SBAT} serves as one of the foundations for the current version.
+The previous version shares the same goal: to create a simple but functional annotation tool that operates entirely in the browser, without any server-side configuration.
+It is implemented using HTML and JavaScript, and can be used to attach user-defined labels to paragraphs.
+It also allows the local import and export of annotation files.
+Building on that, the current version addresses the shortcomings of the previous one by adding functionalities such as span annotations, annotation visualization, and Github support.
 \section{Features}

### 2024-09-05 paper/main.tex
update main part

@@
 \subsection{Interactive User Interface}
-Based on Brat, the annotation UI of SBAT is responsive, interactive and intuitive to use.
-To add an annotation, one can simply double-click or select a span with his mouse, and then select corresponding label in the pop-up window.
-All added labels will be visualized with tags above the annotated text, and different tags differentiate with each other by the user-defined color.
-And if the user has added comments, they will be shown with a mouse hover.
-The size and display of the interface can be adjusted by the option button, and the labels and their style are defined in the JSON config file.
-Besides the main component for annotating text, there is also a step-by-step guide in the beginning for github authentication as well as the export function, all with clear instructions.
+Built upon Brat, the annotation editor of SBAT is responsive, interactive and intuitive.
+To add an annotation, one can simply double-click or select a span with his mouse, and then select the corresponding label in the pop-up menu.
+In the editor, all annotated spans are highlighted with different color, and the added labels are visualized in tags above the annotated span.
+Other user-added comments will become visible with a mouse hover.
+Moreover, the labels and their style can be defined by users in the JSON config file, and the size and display of the editor can be adjusted by the option button.
+Besides the main annotation editor, there is also an area for Github authentication as well as for the the annotation exportation, all guided with clear instructions.
 \subsection{Browser-Based Application}
-SBAT is browser-based, which means one can simply open the website and start annotating in the browser.
-But unlike Brat, all logics of SBAT are completely executed in the browser, there is no need of software installation or server configuration.
-One can either store its front-end files in a Github repository to access it via Github pages online, or download the those files to start it locally in the browser.
-Due to its simple structure, it is fast to run and easy to adapt for different purposes.
+SBAT is browser-based, which means one can access its website and then simply start annotating in the browser.
+But unlike Brat, all logics of SBAT are executed in the browser, so there is no need for software installation or server configuration.
+Due to its simple construction, it is fast to start and convenient to adapt for different purposes.
 \subsection{Github Support}
-SBAT can not only be hosted on Github Pages, but also supports import files from or export annotations to Github repositories.
-To do so, the user only has to enter his Github Personal Access Token (information about the repository name as well as the its owner's user name are entered in advance under "admin config" in the JSON config file), and can then select the github branch as well as the file to open.
-For importing file, all file formats are supported, and they will be treated as txt file, i.e.
-the whole content will be displayed as annotation-ready text in the interface.
-The only exception is JSON file which has been previously exported from SBAT (which has attributes like text, tokens, entities...) -- Their content will be parsed and the annotations saved in the file will be visualized.
-To export annotations, the user can optionally leave a commit message and click the "commit" button, a JSON file with original texts and annotations will be commited to the same Github repository from which the file was originally imported.
-By making use of Github commit, the versions of annotations can be well documented and managed.
+SBAT enables the users to import files from or export annotations to the Github repositories that they have access to.
+To do so, one only has to enter his Github Personal Access Token, and can then select the branch and the filename to open the file in the annotation editor.
+Information about the repository name as well as the repository owner's username should be entered in advance under "admin config" in the JSON config file.
+To export annotations, the user can optionally enter a commit message in the input field and then click the "commit" button.
+By making use of Github commit, the versions of annotations can be well documented and managed.\\
+\\
+For importing files, all file formats are supported, and they will be treated as plain text files, i.e.
+the complete content will be displayed as plain text in the editor for annotation.
+The only exception is the JSON file which has been previously exported from SBAT (which has attributes like text, tokens, entities...) -- Their content will be parsed, and the annotations which have been previously saved in the file will be visualized in the editor.
+And after the user hits the commit button, a JSON file with the original text and its annotations will be committed to the same Github repository from which the file was originally imported.
 \subsection{Project Management Support}
-SBAT's support for Github also provides possibility for user management in annotation projects.
-For instance, the admin can create a Github repository for an annotation project and add the repository and owner information in SBAT's config file.
-By sharing access to this repository with different users, they can contribute to the same project at the same time.
+SBAT's support for Github also enables user management within annotation projects.
+To accept contributions from multiple annotators in an annotation project, the organizer can create a Github repository for the project, and add the repository and owner information in SBAT's config file.
+Then, by sharing access to this repository with members of the annotation project, they can all contribute to the same project.
 Moreover, different branches can be created for different users to create and compare multiple versions.
-This utilization of Github's file management system facilitates the colloboration of multiple annotators in an annotation project.
+The utilization of Github's collaboration features facilitates management of annotation projects.
 \section{Implementation}
-\subsection{Annotation Interface}
-SBAT's annotation interface is rooted in the frontend component from Brat, which is implemented using XHTML, Scalable Vector Graphics (SVG), JavaScript, and jQuery.
-On top of that, to remove the dependance on a server, all user actions such as creating, editing or deleting annotations are handled by the browser.
-This is realized by the LocalAjax class, adapting the LocalAjax function from brat-frontend-editor.
-It locally simulates AJAX requests to process the data without actually sending real network requests.
-Other UI elements, such as the login buttons, are also created by HTML and Asynchronous JavaScript.
-In this way, the complete user interface is embedded in a HTML webpage and all functions are locally executed in the browser.
+\subsection{Annotation UI}
+SBAT's annotation editor is rooted in the frontend component from Brat, which is implemented using XHTML, Scalable Vector Graphics (SVG), JavaScript, and jQuery.
+On top of that, to remove Brat's server-side dependence, the user operations in the editor, such as creating, editing or deleting annotations, are all handled by the browser.
+This is realized by the LocalAjax class, adapting the LocalAjax function from brat-frontend-editor, which locally simulates AJAX requests to process the data without actually sending real network requests.
+Other UI functions, such as the user authentication, are also implemented natively in JavaScript.
+In this way, all components of the user interface are embedded in a HTML webpage and their functionalities are locally executed in the browser.
 \subsection{Browser-Based Construction}
 As SBAT is a static web app without server communications, it can be hosted on Github Pages for free.
-But it is not mandatory to host the app in order to use it, as the index.js file can be used as an entry point to start the app locally in the browser.
-If the users want to access it online instead of locally, the source code can be directly uploaded to a Github repository to host a copy of SBAT on Github Pages.
-Moreover, to cater to different use cases, it is also easy to modify any part of the app -- SBAT uses ECMAScript Modules instead of CommonJS, so all modules are natively loaded in browser and no module bundler such as webpack is used.
-This allows direct modification of individual modules without the need of re-bundling.
+It is not mandatory, though, to host the app on the internet in order to use it, as the index.js file can be used as an entry point to start the app locally in the browser.
+Nonetheless, if the user plans to access it online instead of locally, he can directly upload the source code to his Github repository to host a copy of SBAT on his Github Pages.
+The link can then be shared with others for online access.
+Moreover, to cater to different use cases, it is also easy to modify any part of the app -- SBAT uses ECMAScript Modules instead of CommonJS, so all modules are natively loaded in the browser and no module bundler such as webpack is used.
+This allows direct modification of individual modules without the need for re-bundling.
 \subsection{Usage of Github API}
 SBAT uses Octokit \cite{octokit.js}, the official SDKs for the Github API, which enables the programmatical implementation of Github operations.
-The user authentication through Github Personal Access Token enables creating a new user-authenticated Octokit object and obtaining information about branches and file content from the configured repository.
-Likewise, creating a new commit and pushing to github repository is realized by first obtaining tree of all files from last commit, modifying the changed file or creating a new file, and the creating the new tree and commit it with the REST API endpoint of octokit.
+The user authentication through Github Personal Access Token creates a new user-authenticated Octokit object, which can then be used to obtain information about branches and file content from the user-defined repository.
+Likewise, committing annotations to a Github repository is realized by first obtaining the tree of all files from the last commit in the repository, among the files modifying the changed file or creating a new file, and finally creating a new tree with the updated files and committing it with the REST API endpoint of Octokit.
 
 \section{Conclusion}
-SBAT is an annotation tool that can be used to attach labels to linguistic data.
-It is completely browser-based and only requires a browser to be executed.
-Furthermore, it can be combined well with github to import from and export annotations to user's own github repositories.
-It aims to provide a simpler and no-server solution for annotation projects.\\
+SBAT is an annotation tool for attaching labels to linguistic data, which aims to provide a simpler and no-server solution for annotation projects.
+It is completely browser-based and only requires a browser for usage.
+It retains the essential features of Brat's annotation editor, such as annotation operations and visualizations, while offering integration with Github, enabling user authentication and the import and export of annotations from and to Github repositories.\\
 

### 2024-09-11 index.js
fix selecting file

@@ -1,6 +1,7 @@
 import { BratFrontendEditor } from "./client/src/Brat.js"
 import { Octokit } from "https://esm.sh/octokit@2.1.0";
 
+// get DOM elements
 let patArea = document.getElementById('patArea')
 let branchSelectArea = document.getElementById('branchSelectArea')
 let fileSelectArea = document.getElementById('fileSelectArea')
@@ -18,6 +19,7 @@ let commitMessage = document.getElementById('commitMessage');
 let filePathArea = document.getElementById('filePathArea');
 let filePathInfo = document.getElementById('filePathInfo')
 
+// initialize variables
 let pat;
 let octokit;
 let branches;
@@ -28,21 +30,8 @@ let text;
 let brat;
 let repoName;
 let repoOwner;
-
-
-branchSelectArea.hidden = true;
-fileSelectArea.hidden = true;
-commitArea.hidden = true;
-showDocButton.hidden = true;
-filePathArea.hidden = true;
-
-
-authenticationButton.addEventListener('click', authenticationButtonClicked);
-branchSelectButton.addEventListener('click', getBranchFiles);
-fileSelectButton.addEventListener('click', getFileContent);
-commitConfirmButton.addEventListener('click', pushCommit);
-
-
+let collData;
+// annotated text shown in the start page
 let docData = {
     "messages": [], "source_files": ["txt"], "modifications": [], "normalizations": [], "ctime": 0, "text": "This is an example of how your annotation will look like.\nUpload a txt or json file to start annotating your own text.\nDouble-click or select any span to add your annotation.",
     "entities": [["N1", "Object", [[11, 18]]], ["N2", "Child", [[67, 70]]], ["N3", "Baby", [[74, 78]]]], "attributes": [], "relations": [], "triggers": [["T1", "Assassination", [[119, 131]]], ["T2", "Bomb", [[135, 141]]]], "events": [["E1", "T1", []], ["E2", "T2", []]], "comments": [],
@@ -50,22 +39,30 @@ let docData = {
     [87, 92], [93, 103], [104, 108], [109, 112], [113, 118], [119, 131], [132, 134], [135, 141], [142, 145], [146, 150], [151, 153], [154, 157], [158, 162], [163, 174]]
 }
 
-let collData;
+// hide unwanted areas in the beginning
+branchSelectArea.hidden = true;
+fileSelectArea.hidden = true;
+commitArea.hidden = true;
+showDocButton.hidden = true;
[…]

### 2024-09-13 paper/main.tex
expand introduction

@@
 % \includepdf[pages=-]{name-of-anti-plagiarism-statement-file}
-
+\newpage
+\section*{\centering{Abstract}}
+This paper introduces SBAT, a lightweight and easy-to-use web annotation tool.
+It supports annotation tasks that require attaching labels to text data, such as POS tagging or labeling for named entity recognition.
+Various apps have been developed for the purpose of text annotation, but they often require a dedicated server or a local installation, which complicates the usage.
+Therefore, SBAT is designed to be an online annotation tool that is easy to access and simple to use.
+It is built on the Brat annotation interface, but is completely browser-based and server-free, while preserving most of the key functionalities.
+Additionally, it includes support for integration with Github's file management system.
 \newpage
@@
 \section{Introduction}
-This paper introduces SBAT, a lightweight and easy-to-use web annotation tool.
-It supports annotation tasks that require attaching labels to text data, such as POS tagging or labeling for named entity recognition.
-Various apps have been developed for the purpose of text annotation, but they often require a dedicated server or a local installation, which complicates the usage.
-Therefore, SBAT is designed to be an online annotation tool that is easy to access and simple to use.
-It is built on the Brat annotation interface, but is completely browser-based and server-free, while preserving most of the key functionalities.
-Additionally, it includes support for integration with Github's file management system.
+In computational linguistics, annotating linguistic data has been a crucial step for many studies, based on which it is possible to examine patterns, study linguistic phenomena, train statistical models or testify linguistic theories.
+And among all types of linguistic data, text annotation is the most prevalent.
+Text annotation refers to the labeling or classifying of text data, which is then used for various purposes.
+For instance, the text data with named entities tags can be used to train a NER (named entity recognition) model for Natural Language Processing.
+But annotating is not limited to named entities, tagging semantic roles, dependencies, parts of speech, sentiments, relations and so on are all considered text annotations in common sense.
+Moreover, although automatic annotations by the computer achieved good performance in some cases, most annotation tasks still require the annotation or validation of human annotators, highlighting the necessity of annotation tools.\\
+\\
+For manual or computer-assisted creations of annotated data, a variety of applications have been developed over the years, each with a specific focus or for a specific annotation scheme.
+These tools can recognize spans of characters and their links, and enable the user to associate labels to those spans and links \citep{inbook}.
+Notable examples include BRAT for text span annotation and relation annotation, UD Annotatrix for Universal Dependencies annotation, and INCEpTION for Semantic annotation.
+These tools not only provide an editor-like user interface for annotating operations, but many also enable suggestions generated by machine-learning models to speed up the annotation creation and increase the accuracy.
+Designed for usage in annotation projects, most of them provide user management functionalities through user registration and role assignment, in order to facilitate collaboration of annotators in the annotation process.
+In terms of usage, many of those tools are dependent on Java or Python libraries, and therefore require installation of Java or Python prior to use.
+Some of them have a browser-based frontend, while others are desktop applications.\\
+\\
+While those existing annotation tools provide various solutions across different schemes for the conduction of annotation projects, they often require complicated configuration on either local devices or the server side \citep{yang2018yeddalightweightcollaborativetext}, which is not ideal for smaller annotation projects with limited time and low budget.
+Furthermore, most of them do not have an efficient version control system, which means keeping track of changes or reverting back to previous versions is either impossible or requires a lot of effort.
+Taking those limitations into account, SBAT is designed to be a browser-only, lightweight text span annotation tool, with integrated support for reading and writing files from and to Github repositories.
+By making SBAT browser-based, its only software dependency is a web browser, which is already available on every modern computer.
+And its support for Github repository operations opens the door to the application of Github's version management functionalities in the annotation project.\\
+\\
+The rest of this paper is therefore divided into four sections, each dedicated to the introduction and discussion of annotation tools and SBAT.
+The second chapter deals with the related work in the field, presenting a few representative annotation tools developed over the years, along with an overview of their functionalities, advantages and limitations.
+The third chapter introduces the main features of SBAT, such as its interactive user interface and its support for Github, backed up with detailed instructions and illustrations.
+Following that, the fourth chapter talks about the implementation details in the development of SBAT.
+Finally, this paper ends with concluding remarks about SBAT, pointing out its strength and limitations.
 
+\newpage
 \section{Related Work}
-Among the annotation tools, Brat \cite{stenetorp-etal-2012-brat} is a powerful scheme-neutral annotation tool with an intuitive user interface.
+Among the annotation tools, BRAT \citep{stenetorp-etal-2012-brat} is a powerful scheme-neutral annotation tool with an intuitive user interface.
 Brat can be used for tasks including but not limited to POS tagging, named entity recognition, semantic role labeling, dependency and verb-frame annotations, and enables user-defined constraints-checking.
@@
 \\
-Despite the success of Brat, it is not the simplest tool to start using.
+Despite the success of BRAT, it is not the simplest tool to start using.
 A CGI-capable server is required by its installation, in order to combine all user modifications in real-time with the stored data.
-That is where brat-frontend-editor \cite{brat-frontend-editor}, a forked project of Brat, differentiates itself from the original project.
+That is where brat-frontend-editor \citep{brat-frontend-editor}, a forked project of Brat, differentiates itself from the original project.
 Brat-frontend-editor is a standalone browser version of Brat that keeps some of its essential editing functions but removes its server-side code.
@@
 While Brat serves as a general-purpose annotation tool, more recent tools target specific annotation schemes.
-UD Annotatrix \cite{tyers-etal-2017-ud}, for example, is specifically designed for annotations of universal dependencies.
+UD Annotatrix \citep{tyers-etal-2017-ud}, for example, is specifically designed for annotations of universal dependencies.
 It accepts several input formats including plain text and CoNNL-U, and offers graphical editing functions.
@@
 \\
-Another specialized annotation tool is INCEpTION \cite{klie-etal-2018-inception}, which is used for semantic annotation.
+Another specialized annotation tool is INCEpTION \citep{klie-etal-2018-inception}, which is used for semantic annotation.
 One of its characteristics is the extensive adoption of machine-learning models to assist the annotation process.
@@
 \\
-Lastly, the previous version of SBAT \cite{SBAT} serves as one of the foundations for the current version.
+Lastly, the previous version of SBAT \citep{SBAT} serves as one of the foundations for the current version.
 The previous version shares the same goal: to create a simple but functional annotation tool that operates entirely in the browser, without any server-side configuration.
@@
 Building on that, the current version addresses the shortcomings of the previous one by adding functionalities such as span annotations, annotation visualization, and Github support.
+\newpage
 \section{Features}
@@
 The utilization of Github's collaboration features facilitates management of annotation projects.
+\newpage
 \section{Implementation}
@@
 Likewise, committing annotations to a Github repository is realized by first obtaining the tree of all files from the last commit in the repository, among the files modifying the changed file or creating a new file, and finally creating a new tree with the updated files and committing it with the REST API endpoint of Octokit.
-
+\newpage
 \section{Conclusion}
@@
 
+\newpage
 \bibliography{bibliography}
-\bibliographystyle{plain}
+\bibliographystyle{plainnat}
 

### 2024-09-14 index.js
improve error messages

@@ -86,7 +86,7 @@ fetch('./config.json')
             console.log("personal access token found in local storage")
         }
     })
-    .catch((err) => console.error(`error initializing annotation editor: ${err}`))
+    .catch((err) => window.alert(`error initializing annotation editor: ${err}`))
 
 // function to start annotation editor
 function initializeBrat() {
@@ -96,6 +96,7 @@ function initializeBrat() {
     });
 }
 
+// function to update content in editor with a txt file
 function loadTxt(textData) {
     console.log("loadTxt")
     docData = {
@@ -116,6 +117,7 @@ function loadTxt(textData) {
     updateBratEditor()
 }
 
+// function to update content in editor with a json file
 function loadJson(data) {
     console.log("loadJson")
     let parsedJson = JSON.parse(data);
@@ -146,7 +148,12 @@ async function getRepoBranches() {
         makeBranchDropdown()
         console.log(branches)
     } catch (error) {
-        console.error('Error fetching repo list:', error)
+        window.alert(`Error fetching branches from the repository, please check if the following information is correct:\n
+            repository owner: ${repoOwner}\n
+            repository name: ${repoName}\n
+            error message: ${error}\n
+            Hint: if all information is correct, it could be that you do not have permission to access the repository
+            `)
     }
 }
 
@@ -191,7 +198,7 @@ async function authenticationButtonClicked() {
 }
 
 /* 
-retrieve name of files from the specified branch
+retrieve name of files from the user-specified branch
 and make a drop down list with them
 */
 async function getBranchFiles() {
@@ -211,7 +218,14 @@ async function getBranchFiles() {
         branchSelectArea.hidden = true;
         fileSelectArea.hidden = false;
     } catch (error) {
-        console.error('Error fetching file list:', error)
+        window.alert(`Error fetching files from the branch, please check if the following information is correct:\n
+            repository owner: ${repoOwner}\n
+            repository name: ${repoName}\n
+            file path: /\n
+            branch: ${branch}\n
+            error message: ${error}\n
+            Hint: if all information is correct, it could be that you do not have permission to access the branch
+            `)
     }
 }
 
@@ -238,7 +252,14 @@ async function getFileContent() {
         fileSelectArea.hidden = true;
         bratArea.hidden = false;
     } catch (error) {
-        console.error('Error fetching file content:', error)
+        window.alert(`Error fetching file content, please check if the following information is correct:\n
+            repository owner: ${repoOwner}\n
[…]

### 2024-09-14 index.js
add comments

@@ -69,15 +69,18 @@ fetch('./config.json')
             if (configData.admin_config.branch) {
                 branch = configData.admin_config.branch;
             }
+            /* if the document is still loading, only initialize Brat after loaded,
+            otherwise, initialize Brat straight away */
             if (document.readyState === 'loading') {
                 console.log("loading")
-                // The document is still loading, so add an event listener
                 document.addEventListener('DOMContentLoaded', initializeBrat)
             } else {
                 console.log("loaded")
                 initializeBrat()
             }
         })
+    /* if there is already personal access token saved in localStorage, skip the
+    prompting and authenticate the user with the saved pat right away */
     .then(() => {
         if (localStorage.getItem("personalAccessToken") != null) {
             personalAccessToken.value = localStorage.getItem("personalAccessToken")
@@ -96,7 +99,7 @@ function initializeBrat() {
     });
 }
 
-// function to update content in editor with a txt file
+// update content in Brat editor with a txt file
 function loadTxt(textData) {
     console.log("loadTxt")
     docData = {
@@ -117,7 +120,7 @@ function loadTxt(textData) {
     updateBratEditor()
 }
 
-// function to update content in editor with a json file
+// update Brat content in editor with a json file
 function loadJson(data) {
     console.log("loadJson")
     let parsedJson = JSON.parse(data);
@@ -132,6 +135,7 @@ function loadJson(data) {
 
 }
 
+// use the dispatcher to update the content to display in Brat editor
 function updateBratEditor() {
     if (brat) {
         brat.dispatcher.post('requestRenderData', [docData]);
@@ -139,6 +143,8 @@ function updateBratEditor() {
     }
 }
 
+/* retrieve all existing branches of the given repository
+and make a drop down list with them */
 async function getRepoBranches() {
     try {
         branches = await octokit.rest.repos.listBranches({
@@ -157,6 +163,7 @@ async function getRepoBranches() {
     }
 }
 
+// make a drop down list with all branch options
 const makeBranchDropdown = () => {
     branchSelect.innerHTML = '';
     branches.forEach(branch => {
@@ -167,6 +174,7 @@ const makeBranchDropdown = () => {
     });
 }
 
+// make a drop down list with all file options
 const makeFileDropdown = () => {
     fileSelect.innerHTML = '';
     files.forEach(file => {
@@ -177,24 +185,38 @@ const makeFileDropdown = () => {
     });
 }
 
+// click handler for authentication button
 async function authenticationButtonClicked() {
[…]

### 2024-09-15 index.js
update comments $ error handling

@@ -2,22 +2,23 @@ import { BratFrontendEditor } from "./client/src/Brat.js"
 import { Octokit } from "https://esm.sh/octokit@2.1.0";
 
 // get DOM elements
-let patArea = document.getElementById('patArea')
-let branchSelectArea = document.getElementById('branchSelectArea')
-let fileSelectArea = document.getElementById('fileSelectArea')
+let patArea = document.getElementById('patArea');
+let branchSelectArea = document.getElementById('branchSelectArea');
+let fileSelectArea = document.getElementById('fileSelectArea');
 let personalAccessToken = document.getElementById('personalAccessToken');
 let authenticationButton = document.getElementById('authenticationButton');
 let branchSelect = document.getElementById('branchSelect');
 let branchSelectButton = document.getElementById('branchSelectButton');
 let fileSelect = document.getElementById('fileSelect');
 let fileSelectButton = document.getElementById('fileSelectButton');
-let commitArea = document.getElementById('commitArea')
+let commitArea = document.getElementById('commitArea');
 let commitConfirmButton = document.getElementById('commitConfirmButton');
 let bratArea = document.getElementById('bratArea');
 let showDocButton = document.getElementById('showDocButton');
 let commitMessage = document.getElementById('commitMessage');
 let filePathArea = document.getElementById('filePathArea');
-let filePathInfo = document.getElementById('filePathInfo')
+let filePathInfo = document.getElementById('filePathInfo');
+let message = document.getElementById('message');
 
 // initialize variables
 let pat;
@@ -31,12 +32,18 @@ let brat;
 let repoName;
 let repoOwner;
 let collData;
-// annotated text shown in the start page
+
+// pre-define annotated text shown in the start page
 let docData = {
-    "messages": [], "source_files": ["txt"], "modifications": [], "normalizations": [], "ctime": 0, "text": "This is an example of how your annotation will look like.\nUpload a txt or json file to start annotating your own text.\nDouble-click or select any span to add your annotation.",
-    "entities": [["N1", "Object", [[11, 18]]], ["N2", "Child", [[67, 70]]], ["N3", "Baby", [[74, 78]]]], "attributes": [], "relations": [], "triggers": [["T1", "Assassination", [[119, 131]]], ["T2", "Bomb", [[135, 141]]]], "events": [["E1", "T1", []], ["E2", "T2", []]], "comments": [],
[…]

### 2024-09-21 paper/main.tex
expand main content

@@
 \usepackage{natbib}
-
+\usepackage{setspace}
 \usepackage[margin=1.25in]{geometry}
@@
 \section*{\centering{Abstract}}
+In computational linguistics, annotating linguistic data is a crucial step for many studies, and many tools can be used to facilitate creation of annotated data.
 This paper introduces SBAT, a lightweight and easy-to-use web annotation tool.
 It supports annotation tasks that require attaching labels to text data, such as POS tagging or labeling for named entity recognition.
-Various apps have been developed for the purpose of text annotation, but they often require a dedicated server or a local installation, which complicates the usage.
-Therefore, SBAT is designed to be an online annotation tool that is easy to access and simple to use.
+Among the various applications previously developed for the purpose of text annotation, many require a dedicated server or a local installation, which complicates the usage.
+In contrary, SBAT is designed to be an online annotation tool that is easy to access and simple to use.
 It is built on the Brat annotation interface, but is completely browser-based and server-free, while preserving most of the key functionalities.
@@
 \tableofcontents
+\newpage
 %\listoftables
-%\listoffigures
+\listoffigures
 \newpage
@@
 \section{Introduction}
-In computational linguistics, annotating linguistic data has been a crucial step for many studies, based on which it is possible to examine patterns, study linguistic phenomena, train statistical models or testify linguistic theories.
+Annotated data serves as the foundation for many linguistic studies, based on which it is possible to examine patterns, study linguistic phenomena, train statistical models or testify linguistic theories.
 And among all types of linguistic data, text annotation is the most prevalent.
@@
 Furthermore, most of them do not have an efficient version control system, which means keeping track of changes or reverting back to previous versions is either impossible or requires a lot of effort.
-Taking those limitations into account, SBAT is designed to be a browser-only, lightweight text span annotation tool, with integrated support for reading and writing files from and to Github repositories.
+Taking those limitations into account, SBAT\footnote{Github repository: https://github.com/jiasheng1100/SBAT} is designed to be a browser-only, lightweight text span annotation tool, with integrated support for reading and writing files from and to Github repositories.
 By making SBAT browser-based, its only software dependency is a web browser, which is already available on every modern computer.
@@
 \\
-The rest of this paper is therefore divided into four sections, each dedicated to the introduction and discussion of annotation tools and SBAT.
+The rest of this paper is therefore divided into four sections, all dedicated to the introduction and discussion of annotation tools and SBAT.
 The second chapter deals with the related work in the field, presenting a few representative annotation tools developed over the years, along with an overview of their functionalities, advantages and limitations.
@@
 Among the annotation tools, BRAT \citep{stenetorp-etal-2012-brat} is a powerful scheme-neutral annotation tool with an intuitive user interface.
-Brat can be used for tasks including but not limited to POS tagging, named entity recognition, semantic role labeling, dependency and verb-frame annotations, and enables user-defined constraints-checking.
-It provides a high-quality visualization of annotations by its browser-based UI component implemented in XHTML, Scalable Vector Graphics (SVG) and JavaScript.
+It can be used for tasks including but not limited to POS tagging, named entity recognition, semantic role labeling, dependency and verb-frame annotations, and enables user-defined constraints-checking.
+Moreover, it provides a high-quality visualization of annotations by its browser-based UI component implemented in XHTML, Scalable Vector Graphics (SVG) and JavaScript.
 Last but not least, Brat integrats a ML-based semantic class disambiguator that outputs multiple annotations with their possibility estimates, which has been proven to increase the efficiency of annotators in several annotation projects.\\
 \\
-Despite the success of BRAT, it is not the simplest tool to start using.
+Despite the success of BRAT, it is not the simplest tool to start annotating with.
 A CGI-capable server is required by its installation, in order to combine all user modifications in real-time with the stored data.
@@
 \\
-While Brat serves as a general-purpose annotation tool, more recent tools target specific annotation schemes.
+While BRAT serves as a general-purpose annotation tool, more recent tools target specific annotation schemes.
 UD Annotatrix \citep{tyers-etal-2017-ud}, for example, is specifically designed for annotations of universal dependencies.
 It accepts several input formats including plain text and CoNNL-U, and offers graphical editing functions.
-Unlike Brat, it offers a stand-alone module written in JavaScript with locally saved dependencies, which stores imported corpora in localStorage and allows offline usage.
-Otherwise, there is also a server module to save corpora on the server.\\
+Unlike BRAT, it offers a stand-alone module written in JavaScript with locally saved dependencies, which stores imported corpora in localStorage and allows offline usage.
+Otherwise, there is also a server module, which saves corpora on the server when enabled.\\
 \\
-Another specialized annotation tool is INCEpTION \citep{klie-etal-2018-inception}, which is used for semantic annotation.
+Another domain-specific annotation platform is INCEpTION \citep{klie-etal-2018-inception}, which specializes in semantic annotation.
 One of its characteristics is the extensive adoption of machine-learning models to assist the annotation process.
-It not only utilizes recommenders based on machine learning models to provide users with suggestions for possible labels, but also provides an active learning mode where user feedback can be used to further improve the quality of those suggestions.
+It not only utilizes recommenders based on trained models to provide users with suggestions for possible labels, but also provides an active learning mode where user feedback can be used to further improve the quality of those suggestions.
 It also has a comprehensive user management system, where the admin can create multiple user accounts for the project and assign them different roles.
@@
 The previous version shares the same goal: to create a simple but functional annotation tool that operates entirely in the browser, without any server-side configuration.
-It is implemented using HTML and JavaScript, and can be used to attach user-defined labels to paragraphs.
+It is implemented using HTML and JavaScript, and can be used to attach user-defined labels to whole texts.
 It also allows the local import and export of annotation files.
-Building on that, the current version addresses the shortcomings of the previous one by adding functionalities such as span annotations, annotation visualization, and Github support.
+Building on that, the current version addresses the limitations of the previous one by adding functionalities such as span annotations, annotation visualization, and Github support.
 \newpage
@@
 \subsection{Interactive User Interface}
-Built upon Brat, the annotation editor of SBAT is responsive, interactive and intuitive.
-To add an annotation, one can simply double-click or select a span with his mouse, and then select the corresponding label in the pop-up menu.
-In the editor, all annotated spans are highlighted with different color, and the added labels are visualized in tags above the annotated span.
-Other user-added comments will become visible with a mouse hover.
-Moreover, the labels and their style can be defined by users in the JSON config file, and the size and display of the editor can be adjusted by the option button.
+Built upon BRAT, the annotation editor of SBAT is responsive, interactive and intuitive.
+To add an annotation, one can simply double-click or drag to select a span of characters with his mouse.
+A pop-up window will then appear [\hyperref[figure1]{Figure 1}], with a list of options of labels that the user has pre-defined in the config file.
+The user can then select the corresponding label in the pop-up menu, click the "OK" button, and the selected label is added as an annotation.
+In the editor, all annotated spans are highlighted with different color, and the appended labels are visualized in tags above the spans [\hyperref[figure2]{Figure 2}].
+If there is any unclarity, users can also add their comments to the span, which will become visible with a mouse hover.
+Moreover, the label options and their styles can be defined by users in the JSON config file, and the size and display of the editor can be adjusted by the option button.
 Besides the main annotation editor, there is also an area for Github authentication as well as for the the annotation exportation, all guided with clear instructions.
+\begin{figure}[H]
+{\centering
+\includegraphics[scale=0.55]{addNewAnnotation.png}
+\label{figure1}
+\caption{Pop-Up Menu for New Annotation}
+}
+{\setstretch{1.0}\scriptsize Appears when double-clicking or dragging to select a span of text in the editor.
+The displayed options are defined in the config file, in this case two entity types, "Person" and "Object".\par}
+\end{figure}
+\subsection{Github Support}
+SBAT enables the users to import files from or export annotations to the Github repositories that they have access to.
+To do so, one only has to enter his Github Personal Access Token, and can then select the branch and the filename to open the file in the annotation editor.
+To export annotations, the user can optionally enter a commit message in the input field and then click the "commit" button.
+In the whole process, if any error occurs in any step, the user will be prompted with the error message with hints to fix it, or, in terms of successful commit, also a message that indicates success.
+And by making use of Github commit, the versions of annotations can be well documented and managed.\\
+\\
+For importing files, all file formats are supported, and they will be treated as plain text files, i.e.
+the complete content will be displayed as plain text in the editor for annotation.
+The only exception is the JSON file which has been previously exported from SBAT.
+These JSON files have standard attributes including text, tokens, entities, and so on, and when imported in SBAT, their attribute values will be parsed, and the annotations which have been previously saved in the file will be visualized in the editor [\hyperref[figure2]{Figure 2}].
+And after the user hits the commit button, a JSON file with the original text and its annotation meta data will be committed to the same Github repository from which the file was originally imported.
+One example of such SBAT-generated json files can be found in the "example data" folder.
+
+\begin{figure}[H]
+{\centering
+\includegraphics[scale=0.55]{visualization.png}
+\label{figure2}
+\caption{Visualization of Annotations}
+}
+{\setstretch{1.0}\scriptsize Annotations can be exported into a JSON file, and when loading this file in SBAT, all previous annotations will be visualized in the editor.\par}
+\end{figure}
+
+SBAT's support for Github also enables user management within annotation projects.
+To accept contributions from multiple annotators in an annotation project, the organizer can create a Github repository for the project and share its access with project members.
+By doing so, all members can contribute to the same project.
+Moreover, different branches can be created for different users to create and compare multiple versions.
+The utilization of Github's collaboration features facilitates in this way management of annotation projects.
+
 \subsection{Browser-Based Application}
@@
 But unlike Brat, all logics of SBAT are executed in the browser, so there is no need for software installation or server configuration.
+Furthermore, by making use of the localStorage of the browser, SBAT can save the user's Personal Access Token once logged in, and automatically log the user in with the same token next time when the site is started in the same browser.
+This is to simplify the log in process and to allow user to concentrate on annotation tasks.
+If the user then wishes to log in with a different token, he can utilize the "clear history" function of the browser to clear the previously saved token.
 Due to its simple construction, it is fast to start and convenient to adapt for different purposes.
-\subsection{Github Support}
-SBAT enables the users to import files from or export annotations to the Github repositories that they have access to.
-To do so, one only has to enter his Github Personal Access Token, and can then select the branch and the filename to open the file in the annotation editor.
-Information about the repository name as well as the repository owner's username should be entered in advance under "admin config" in the JSON config file.
-To export annotations, the user can optionally enter a commit message in the input field and then click the "commit" button.
-By making use of Github commit, the versions of annotations can be well documented and managed.\\
-\\
-For importing files, all file formats are supported, and they will be treated as plain text files, i.e.
-the complete content will be displayed as plain text in the editor for annotation.
-The only exception is the JSON file which has been previously exported from SBAT (which has attributes like text, tokens, entities...) -- Their content will be parsed, and the annotations which have been previously saved in the file will be visualized in the editor.
-And after the user hits the commit button, a JSON file with the original text and its annotations will be committed to the same Github repository from which the file was originally imported.
-\subsection{Project Management Support}
-SBAT's support for Github also enables user management within annotation projects.
-To accept contributions from multiple annotators in an annotation project, the organizer can create a Github repository for the project, and add the repository and owner information in SBAT's config file.
-Then, by sharing access to this repository with members of the annotation project, they can all contribute to the same project.
-Moreover, different branches can be created for different users to create and compare multiple versions.
-The utilization of Github's collaboration features facilitates management of annotation projects.
+
+\subsection{Flexible Configuration}
+Configuration of SBAT is allowed in the config.json file, which makes it easy for users to customize and tailor it to different tasks.
+For importing files from GitHub, the user is able to enter repository name, owner, branch and file name under the "admin config" attribute in advance, which will allow SBAT to skip the intermediate file selection process in every start [\hyperref[figure3]{Figure 3}] and to directly redirect the user to the editing page of the specified file.
+This also serves as a solution for importing files that are not located in the first level of the repository but in folders, as it can then not be directly found by user's manual selection.
+In this case, by
+providing the complete path of the file in the config file, e.g. "folder1/folder3/example.json", the user can easily find and open any file that is located in deeper folder structures. \\
+\begin{figure}[H]
+{\centering
+\includegraphics[scale=0.55]{selectFile.png}
+\label{figure3}
+\caption{Drop-Down List for File Selection}
+}
+{\setstretch{1.0}\scriptsize The "branch" and "filePath" attributes in "admin config" are optional.
+If no value is provided, SBAT will prompt user with a drop-down list with available branches or files to select from.\par}
+\end{figure}
+Details about annotation labels are also defined in the config file.
+For example, the user can define multiple entity types, their attributes, their children, and the background color for visualization when annotated.
+They will then appear in the pop-up menu as available options when the user adds a new annotation in the editor [\hyperref[figure1]{Figure 1}].
+Besides entity types, there are also event types, event attribute types, relation types, and relation attribute types that can be defined for annotations, each for different annotating tasks.
+A more complete example of definition of such types can be found in the config.json file in "example data" folder.
+
 \newpage
@@
 This is realized by the LocalAjax class, adapting the LocalAjax function from brat-frontend-editor, which locally simulates AJAX requests to process the data without actually sending real network requests.
-Other UI functions, such as the user authentication, are also implemented natively in JavaScript.
+Other UI functions, such as the user authentication, import and export functions, are also implemented natively in JavaScript.
 In this way, all components of the user interface are embedded in a HTML webpage and their functionalities are locally executed in the browser.
@@
 As SBAT is a static web app without server communications, it can be hosted on Github Pages for free.
-It is not mandatory, though, to host the app on the internet in order to use it, as the index.js file can be used as an entry point to start the app locally in the browser.
+It is not mandatory, though, to host the app on the internet in order to use it, as the index.html file can be used as an entry point to start the app locally in the browser.
 Nonetheless, if the user plans to access it online instead of locally, he can directly upload the source code to his Github repository to host a copy of SBAT on his Github Pages.
-The link can then be shared with others for online access.
-Moreover, to cater to different use cases, it is also easy to modify any part of the app -- SBAT uses ECMAScript Modules instead of CommonJS, so all modules are natively loaded in the browser and no module bundler such as webpack is used.
+The link to the hosted website can then be shared with others for online access.
+Moreover, to cater to different use cases, it is also easy to modify any part of the app -- SBAT replaces the client-side CommonJS modules of BRAT with ECMAScript modules, so all modules are natively loaded in the browser and no module bundler such as webpack is used.
 This allows direct modification of individual modules without the need for re-bundling.
 \subsection{Usage of Github API}
-SBAT uses Octokit \cite{octokit.js}, the official SDKs for the Github API, which enables the programmatical implementation of Github operations.
-The user authentication through Github Personal Access Token creates a new user-authenticated Octokit object, which can then be used to obtain information about branches and file content from the user-defined repository.
+SBAT uses Octokit \footnote{https://esm.sh/octokit@2.1.0, last accessed on September 20th, 2024}, the official SDKs for the Github API, which enables the programmatical implementation of Github operations.
+The user authentication through Github Personal Access Token creates a new user-authenticated Octokit object, which can then be used to obtain information about branches and file content from GitHub repositories that the authenticated user has access to.
 Likewise, committing annotations to a Github repository is realized by first obtaining the tree of all files from the last commit in the repository, among the files modifying the changed file or creating a new file, and finally creating a new tree with the updated files and committing it with the REST API endpoint of Octokit.
+Besides, error handling is implemented for every API call, which catches any potential error and prompts the user with informative error messages and hints.\\
+\\
+During development, a test Github Personal Access Token is generated under GitHub -> Settings -> Developer Settings -> Personal access tokens.
+As SBAT only performs the absolutely necessary operations with GitHub authenticated access, which are retrieving list of branches and file names of a repository, obtaining file content, getting information about last commit, and creating new commit, the scope of the Personal Access Token generated for SBAT only needs to cover the repository operations under "Full control of private repositories".
 \newpage
 \section{Conclusion}
-SBAT is an annotation tool for attaching labels to linguistic data, which aims to provide a simpler and no-server solution for annotation projects.
-It is completely browser-based and only requires a browser for usage.
-It retains the essential features of Brat's annotation editor, such as annotation operations and visualizations, while offering integration with Github, enabling user authentication and the import and export of annotations from and to Github repositories.\\
-
-%\begin{figure}[H]
-%\centering
-%\includegraphics[scale=0.2]{rag.png}
-%\caption{Retrieval Augmented Generation}
-%Source: https://techcommunity.microsoft.com/t5/azure-ai-services-blog/revolutionize-your-enterprise-data-with-chatgpt-next-gen-apps-w/ba-p/3762087
-%\end{figure}
+Text annotation is an important task in linguistic studies, and there have been various applications developed to assist the annotation process.
+They provide editor-like user interfaces, designed for general or specific annotation tasks according to different annotation schemes.
+Many of them also adopt machine-learning models to further speed up manual annotation or validation, and provide support for user management in annotation projects.
+However, they mostly requires complicated local or server-side configuration, which increases the cost and time for starting an annotation project.\\
+\\
+To address that limitation, SBAT aims to provide a simpler and no-server solution for annotation projects.
+It is an annotation tool for attaching labels to text spans, and is completely browser-based and only requires a browser to function, as its functionalities are all implemented in JavaScript and locally executed.
+It retains the essential features of BRAT's annotation editor, such as annotation operations and visualizations, while offering integration with Github, enabling and the import and export of annotations from and to user-authenticated Github repositories.
+Although its usage is currently limited to text span annotation, it can be easily adapted or extended to accomodate the needs of different annotation tasks due to its modular structure and flexible configuration.\\
 

### 2024-09-22 paper/main.tex
improve error message & paper

@@
 \section*{\centering{Abstract}}
-In computational linguistics, annotating linguistic data is a crucial step for many studies, and many tools can be used to facilitate creation of annotated data.
+In computational linguistics, annotating linguistic data is a crucial step for many studies, and many tools can be used to facilitate the creation of annotated data.
 This paper introduces SBAT, a lightweight and easy-to-use web annotation tool.
-It supports annotation tasks that require attaching labels to text data, such as POS tagging or labeling for named entity recognition.
+It supports annotation tasks that require attaching labels to text spans, such as POS tagging or labeling for named entity recognition.
 Among the various applications previously developed for the purpose of text annotation, many require a dedicated server or a local installation, which complicates the usage.
-In contrary, SBAT is designed to be an online annotation tool that is easy to access and simple to use.
+On the contrary, SBAT is designed to be an online annotation tool that is easy to access and simple to use.
 It is built on the Brat annotation interface, but is completely browser-based and server-free, while preserving most of the key functionalities.
-Additionally, it includes support for integration with Github's file management system.
+Additionally, it provides support for integration with Github's file management system, which facilitates version control and user management in annotation projects.
 \newpage
@@
 Annotated data serves as the foundation for many linguistic studies, based on which it is possible to examine patterns, study linguistic phenomena, train statistical models or testify linguistic theories.
-And among all types of linguistic data, text annotation is the most prevalent.
-Text annotation refers to the labeling or classifying of text data, which is then used for various purposes.
-For instance, the text data with named entities tags can be used to train a NER (named entity recognition) model for Natural Language Processing.
+And among all types of data, text annotation is the most prevalent.
+Text annotation refers to the labeling or classification of text data, which is then used for various purposes.
+For instance, the text data with named entity tags can be used to train a NER (named entity recognition) model for Natural Language Processing.
 But annotating is not limited to named entities, tagging semantic roles, dependencies, parts of speech, sentiments, relations and so on are all considered text annotations in common sense.
@@
 For manual or computer-assisted creations of annotated data, a variety of applications have been developed over the years, each with a specific focus or for a specific annotation scheme.
-These tools can recognize spans of characters and their links, and enable the user to associate labels to those spans and links \citep{inbook}.
+Those tools can recognize spans of characters and their links, and enable the user to associate labels to those spans and links \citep{inbook}.
 Notable examples include BRAT for text span annotation and relation annotation, UD Annotatrix for Universal Dependencies annotation, and INCEpTION for Semantic annotation.
-These tools not only provide an editor-like user interface for annotating operations, but many also enable suggestions generated by machine-learning models to speed up the annotation creation and increase the accuracy.
-Designed for usage in annotation projects, most of them provide user management functionalities through user registration and role assignment, in order to facilitate collaboration of annotators in the annotation process.
+Those tools not only provide an editor-like user interface for annotating operations, but many also enable suggestions generated by machine-learning models to speed up the creation of annotations and improve accuracy.
+Designed for usage in annotation projects, most of them provide user management functionalities through user registration and role assignment, in order to facilitate the collaboration of annotators in the annotation process.
 In terms of usage, many of those tools are dependent on Java or Python libraries, and therefore require installation of Java or Python prior to use.
-Some of them have a browser-based frontend, while others are desktop applications.\\
+Some of them have a web platform, while others are desktop applications.\\
 \\
 While those existing annotation tools provide various solutions across different schemes for the conduction of annotation projects, they often require complicated configuration on either local devices or the server side \citep{yang2018yeddalightweightcollaborativetext}, which is not ideal for smaller annotation projects with limited time and low budget.
-Furthermore, most of them do not have an efficient version control system, which means keeping track of changes or reverting back to previous versions is either impossible or requires a lot of effort.
-Taking those limitations into account, SBAT\footnote{Github repository: https://github.com/jiasheng1100/SBAT} is designed to be a browser-only, lightweight text span annotation tool, with integrated support for reading and writing files from and to Github repositories.
+Furthermore, most of them do not have an efficient version control system, which means keeping track of changes or reverting to previous versions is either impossible or requires a lot of effort.
+Taking those limitations into account, SBAT\footnote{GitHub repository: https://github.com/jiasheng1100/SBAT} is designed to be a browser-only, lightweight text span annotation tool, with integrated support for reading and writing files from and to GitHub repositories.
 By making SBAT browser-based, its only software dependency is a web browser, which is already available on every modern computer.
-And its support for Github repository operations opens the door to the application of Github's version management functionalities in the annotation project.\\
+And its support for GitHub repository operations opens the door to the adoption of GitHub's version management functionalities in annotation projects.\\
 \\
-The rest of this paper is therefore divided into four sections, all dedicated to the introduction and discussion of annotation tools and SBAT.
-The second chapter deals with the related work in the field, presenting a few representative annotation tools developed over the years, along with an overview of their functionalities, advantages and limitations.
-The third chapter introduces the main features of SBAT, such as its interactive user interface and its support for Github, backed up with detailed instructions and illustrations.
-Following that, the fourth chapter talks about the implementation details in the development of SBAT.
-Finally, this paper ends with concluding remarks about SBAT, pointing out its strength and limitations.
+The rest of this paper is therefore divided into four sections, all dedicated to the introduction of SBAT and its comparison with the current popular annotation tools.
+The second chapter deals with the relevant works in the field, presenting a few representative annotation tools developed over the years, along with an overview of their functionalities, advantages and limitations.
+The third chapter demonstrates the main features of SBAT, such as its interactive user interface and its support for Github, supplemented with detailed instructions and examples.
+Following that, the fourth chapter talks about the technical details of implementation in the development of SBAT.
+Finally, this paper ends with concluding remarks about SBAT, illustrating its strengths and limitations.
 
@@
 It can be used for tasks including but not limited to POS tagging, named entity recognition, semantic role labeling, dependency and verb-frame annotations, and enables user-defined constraints-checking.
-Moreover, it provides a high-quality visualization of annotations by its browser-based UI component implemented in XHTML, Scalable Vector Graphics (SVG) and JavaScript.
-Last but not least, Brat integrats a ML-based semantic class disambiguator that outputs multiple annotations with their possibility estimates, which has been proven to increase the efficiency of annotators in several annotation projects.\\
+Moreover, it provides a high-quality visualization of annotations through its UI components implemented in XHTML, Scalable Vector Graphics (SVG) and JavaScript.
+Last but not least, BRAT integrates an ML-based semantic class disambiguator that outputs multiple annotations with their possibility estimates, which has been proven to increase the efficiency of annotators in several annotation projects.\\
 \\
@@
 It also has a comprehensive user management system, where the admin can create multiple user accounts for the project and assign them different roles.
-In terms of the software itself, INCEpTION is a Java application with Spring Boot backend and a web user interface, so its usage requires the installation of Java as well as the software.\\
+In terms of the software itself, INCEpTION is a Java application with Spring Boot backend and a web user interface, so its usage requires the installation of Java as well as the software on the local device.\\
 \\
@@
 It also allows the local import and export of annotation files.
-Building on that, the current version addresses the limitations of the previous one by adding functionalities such as span annotations, annotation visualization, and Github support.
+Building on that, the current version addresses the limitations of the previous one by enabling functionalities such as span annotations, editor UI, visualization, and Github support.
 \newpage
@@
 \subsection{Interactive User Interface}
-Built upon BRAT, the annotation editor of SBAT is responsive, interactive and intuitive.
-To add an annotation, one can simply double-click or drag to select a span of characters with his mouse.
-A pop-up window will then appear [\hyperref[figure1]{Figure 1}], with a list of options of labels that the user has pre-defined in the config file.
+Built upon BRAT, the user interface of SBAT is responsive, interactive and intuitive.
+It enables all basic operations in the editor, including creating, editing, or deleting annotations, with dragging and clicking operations of the mouse.
+The size and display of the editor can also be manually toggled by the option button.\\
+\\
+To create a new annotation, one can simply double-click or drag to select a span of characters with his mouse.
+A pop-up window will then appear [\hyperref[figure1]{Figure 1}], with a list of label options that the user has pre-defined in the config file.
 The user can then select the corresponding label in the pop-up menu, click the "OK" button, and the selected label is added as an annotation.
-In the editor, all annotated spans are highlighted with different color, and the appended labels are visualized in tags above the spans [\hyperref[figure2]{Figure 2}].
-If there is any unclarity, users can also add their comments to the span, which will become visible with a mouse hover.
-Moreover, the label options and their styles can be defined by users in the JSON config file, and the size and display of the editor can be adjusted by the option button.
-Besides the main annotation editor, there is also an area for Github authentication as well as for the the annotation exportation, all guided with clear instructions.
+In the editor, all annotated spans are highlighted with different colors, and the appended labels are visualized in tags above the spans [\hyperref[figure2]{Figure 2}].
+If there is any unclarity, users can also add their notes to the span, which will become visible with a mouse hover.\\
+\\
+Likewise, with a double click on a previously added annotation in the editor, a pop-up window will appear that allows the edit or deletion of this annotation.
+For editing, one can select a different label or edit the notes, and then hit the "OK" button.
+The changes will then be saved and displayed in the visualization.
+And for deletion of an annotation, clicking the "Delete" button will do.
+There is also a button for adding a fragment to an existing annotation, which, once clicked, will allow the user to select another text span and add it as a fragment.
+The corresponding fragments will then share the same label, and can be moved or deleted.\\
+\\
+Besides the main annotation editor, there is also an area for GitHub authentication as well as for the import and export of annotation files.
+Depending on whether the user has previously successfully logged in using the current browser and whether the information about file paths has been provided in the config file, the user might be directly redirected to the editing page of an annotation file or will be prompted to provide authentication token and to select the file from a drop-down list [\hyperref[figure3]{Figure 3}].
+All those steps will be guided with clear instructions in the user interface.
 \begin{figure}[H]
@@
 }
-{\setstretch{1.0}\scriptsize Appears when double-clicking or dragging to select a span of text in the editor.
+{\setstretch{1.0}\scriptsize This pop-up window appears when double-clicking or dragging to select a span of text in the editor.
 The displayed options are defined in the config file, in this case two entity types, "Person" and "Object".\par}
@@
 \subsection{Github Support}
-SBAT enables the users to import files from or export annotations to the Github repositories that they have access to.
-To do so, one only has to enter his Github Personal Access Token, and can then select the branch and the filename to open the file in the annotation editor.
+SBAT enables users to import files from or export annotations to the GitHub repositories to which they have access.
+To do so, one only has to enter his Github Personal Access Token, and can then select the branch and the filename -- if not already provided in the config file -- to open the file in the annotation editor.
 To export annotations, the user can optionally enter a commit message in the input field and then click the "commit" button.
 In the whole process, if any error occurs in any step, the user will be prompted with the error message with hints to fix it, or, in terms of successful commit, also a message that indicates success.
-And by making use of Github commit, the versions of annotations can be well documented and managed.\\
+By making use of GitHub commits, the versions of annotations can be well documented and managed.\\
 \\
@@
 the complete content will be displayed as plain text in the editor for annotation.
-The only exception is the JSON file which has been previously exported from SBAT.
-These JSON files have standard attributes including text, tokens, entities, and so on, and when imported in SBAT, their attribute values will be parsed, and the annotations which have been previously saved in the file will be visualized in the editor [\hyperref[figure2]{Figure 2}].
-And after the user hits the commit button, a JSON file with the original text and its annotation meta data will be committed to the same Github repository from which the file was originally imported.
-One example of such SBAT-generated json files can be found in the "example data" folder.
+The only exception is the JSON files which have been previously exported from SBAT.
+These JSON files have standard attributes including text, tokens, entities, and so on, and when imported in SBAT, their attribute values will be parsed, and the annotations saved in the file will be visualized in the editor [\hyperref[figure2]{Figure 2}].\\
 
@@
 
-SBAT's support for Github also enables user management within annotation projects.
-To accept contributions from multiple annotators in an annotation project, the organizer can create a Github repository for the project and share its access with project members.
+For file exports, after the user hits the commit button, a JSON file with the original text and its annotation metadata will be committed to the same GitHub repository from which the file was originally imported.
+One example of such SBAT-generated JSON files can be found in the "example data" folder.
+The JSON format not only enables the visualization of those annotations in SBAT, but also facilitates programmatic parsing for future purposes.\\
+\\
+SBAT's support for GitHub also enables user management within annotation projects.
+To accept contributions from multiple annotators in an annotation project, the organizer can create a GitHub repository for the project and share its access with project members.
 By doing so, all members can contribute to the same project.
-Moreover, different branches can be created for different users to create and compare multiple versions.
-The utilization of Github's collaboration features facilitates in this way management of annotation projects.
+Moreover, separate branches can be created for different users to create and compare multiple versions.
+The utilization of GitHub's collaboration features in this way facilitates the management of annotation projects.
 
 \subsection{Browser-Based Application}
-SBAT is browser-based, which means one can access its website and then simply start annotating in the browser.
+SBAT is browser-based, which means one can access its website to start annotating in the browser.
 But unlike Brat, all logics of SBAT are executed in the browser, so there is no need for software installation or server configuration.
-Furthermore, by making use of the localStorage of the browser, SBAT can save the user's Personal Access Token once logged in, and automatically log the user in with the same token next time when the site is started in the same browser.
-This is to simplify the log in process and to allow user to concentrate on annotation tasks.
-If the user then wishes to log in with a different token, he can utilize the "clear history" function of the browser to clear the previously saved token.
+Furthermore, SBAT makes use of the localStorage of the browser to save the user's Personal Access Token once logged in, and automatically logs the user in the next time when the site is started in the same browser.
+This is to simplify the log-in process and to allow users to concentrate on real annotation tasks.
+If one then wishes to log in with a different token, he can utilize the "clear history" function of the browser to clear the previously saved token.
 Due to its simple construction, it is fast to start and convenient to adapt for different purposes.
@@
 Configuration of SBAT is allowed in the config.json file, which makes it easy for users to customize and tailor it to different tasks.
-For importing files from GitHub, the user is able to enter repository name, owner, branch and file name under the "admin config" attribute in advance, which will allow SBAT to skip the intermediate file selection process in every start [\hyperref[figure3]{Figure 3}] and to directly redirect the user to the editing page of the specified file.
-This also serves as a solution for importing files that are not located in the first level of the repository but in folders, as it can then not be directly found by user's manual selection.
-In this case, by
-providing the complete path of the file in the config file, e.g. "folder1/folder3/example.json", the user can easily find and open any file that is located in deeper folder structures. \\
+For importing files from GitHub, the user is able to enter the repository name, owner, branch and file path under the "admin config" attribute in advance, which will allow SBAT to skip the intermediate file selection process in every start [\hyperref[figure3]{Figure 3}] and to directly display the pre-defined file in the annotation editor.
+This also serves as an alternative solution for importing files that are not located in the first level of the repository but in folders, as they can not be directly found by the user's manual selection.
+In that case, by providing the complete path of the file in the config file, e.g.
+"folder1/folder3/example.json", the user can easily find and open any file that is located in deeper folder structures.
+\\
 \begin{figure}[H]
@@
 {\setstretch{1.0}\scriptsize The "branch" and "filePath" attributes in "admin config" are optional.
-If no value is provided, SBAT will prompt user with a drop-down list with available branches or files to select from.\par}
+If no value is provided, SBAT will prompt the user with a drop-down list with available branch or file names to select from.\par}
 \end{figure}
@@
 Besides entity types, there are also event types, event attribute types, relation types, and relation attribute types that can be defined for annotations, each for different annotating tasks.
-A more complete example of definition of such types can be found in the config.json file in "example data" folder.
+A more complete example of the definition of such types can be found in the config.json file in the "example data" folder.
 
@@
 This is realized by the LocalAjax class, adapting the LocalAjax function from brat-frontend-editor, which locally simulates AJAX requests to process the data without actually sending real network requests.
-Other UI functions, such as the user authentication, import and export functions, are also implemented natively in JavaScript.
-In this way, all components of the user interface are embedded in a HTML webpage and their functionalities are locally executed in the browser.
+Other UI functions, such as user authentication, and import and export functions, are also implemented natively in JavaScript.
+In this way, all functionalities of the user interface are realized in the script files attached to an HTML webpage and are locally executed by the browser.
 \subsection{Browser-Based Construction}
-As SBAT is a static web app without server communications, it can be hosted on Github Pages for free.
+As SBAT is a static web app without server communications, it can be hosted on GitHub Pages for free.
 It is not mandatory, though, to host the app on the internet in order to use it, as the index.html file can be used as an entry point to start the app locally in the browser.
-Nonetheless, if the user plans to access it online instead of locally, he can directly upload the source code to his Github repository to host a copy of SBAT on his Github Pages.
-The link to the hosted website can then be shared with others for online access.
-Moreover, to cater to different use cases, it is also easy to modify any part of the app -- SBAT replaces the client-side CommonJS modules of BRAT with ECMAScript modules, so all modules are natively loaded in the browser and no module bundler such as webpack is used.
-This allows direct modification of individual modules without the need for re-bundling.
+Nonetheless, if the user plans to access it on the web instead of locally, he can directly upload SBAT's source code to his Github repository to host a copy on his Github Pages.
+For the development stage, a copy of SBAT is also hosted on the GitHub Pages, which is done by heading to the SBAT code repository on GitHub -> Settings -> Pages and selecting the option of deploying from the "main" branch.\\
+\\
+Once hosted on the web, its link can be shared with other project members for online access.
+Under that circumstance, it is recommended to leave the "branch" and "filePath" values in the config files empty, so that every project member can select their own branch and file to work on.
+Moreover, to cater to different use cases, it is also easy to modify any part of the app -- SBAT replaces the client-side CommonJS modules of BRAT with ECMAScript modules, so all modules are natively loaded in the browser and no module bundler such as Webpack is used.
+This allows direct modification of each individual component without the need for re-bundling.
 \subsection{Usage of Github API}
-SBAT uses Octokit \footnote{https://esm.sh/octokit@2.1.0, last accessed on September 20th, 2024}, the official SDKs for the Github API, which enables the programmatical implementation of Github operations.
-The user authentication through Github Personal Access Token creates a new user-authenticated Octokit object, which can then be used to obtain information about branches and file content from GitHub repositories that the authenticated user has access to.
-Likewise, committing annotations to a Github repository is realized by first obtaining the tree of all files from the last commit in the repository, among the files modifying the changed file or creating a new file, and finally creating a new tree with the updated files and committing it with the REST API endpoint of Octokit.
-Besides, error handling is implemented for every API call, which catches any potential error and prompts the user with informative error messages and hints.\\
+SBAT uses Octokit \footnote{https://esm.sh/octokit@2.1.0, last accessed on September 20th, 2024}, the official SDKs for the GitHub API, which enables to implement Github operations programmatically.
+The authentication through a user-provided GitHub Personal Access Token creates a new user-authenticated Octokit object, which can be used to obtain data from GitHub repositories to which the authenticated user has access.
+Likewise, committing annotations to a GitHub repository is realized by first obtaining the tree of all files from the last commit in the repository, then updating an existing file with the modifications or creating a new file, and finally creating a new tree with the updated files and committing it with the Octokit's REST API endpoint.
+Moreover, error handling is implemented for every API call, which catches any potential error and prompts the user with informative error messages and hints.\\
 \\
 During development, a test Github Personal Access Token is generated under GitHub -> Settings -> Developer Settings -> Personal access tokens.
-As SBAT only performs the absolutely necessary operations with GitHub authenticated access, which are retrieving list of branches and file names of a repository, obtaining file content, getting information about last commit, and creating new commit, the scope of the Personal Access Token generated for SBAT only needs to cover the repository operations under "Full control of private repositories".
+SBAT only performs the absolutely necessary operations for file access and version control with GitHub authentication, namely retrieving lists of branches and file names under a specified repository, obtaining file content, getting information about the last commit, and creating new commits, so the scope of the Personal Access Token generated for SBAT only needs to cover those basic repository operations under the "Full control of private repositories" section.
 \newpage
@@
 Many of them also adopt machine-learning models to further speed up manual annotation or validation, and provide support for user management in annotation projects.
-However, they mostly requires complicated local or server-side configuration, which increases the cost and time for starting an annotation project.\\
+However, they mostly require complicated local or server-side configuration, which increases the cost and time for starting an annotation project.
+Also, an integrated solution for version management is absent in those tools.\\
 \\
-To address that limitation, SBAT aims to provide a simpler and no-server solution for annotation projects.
-It is an annotation tool for attaching labels to text spans, and is completely browser-based and only requires a browser to function, as its functionalities are all implemented in JavaScript and locally executed.
-It retains the essential features of BRAT's annotation editor, such as annotation operations and visualizations, while offering integration with Github, enabling and the import and export of annotations from and to user-authenticated Github repositories.
-Although its usage is currently limited to text span annotation, it can be easily adapted or extended to accomodate the needs of different annotation tasks due to its modular structure and flexible configuration.\\
+To address those limitations, SBAT aims to provide a simpler and no-server solution for annotation projects.
+It retains the essential features of BRAT's annotation editor, such as annotation operations and visualizations, while offering integration with Github, enabling the import and export of annotations from and to user-authenticated Github repositories.
+Although its usage is currently limited to text span annotation, it can be easily adapted or extended to accommodate the needs of different annotation tasks due to its modular structure and flexible configuration.\\
 

### 2024-09-22 index.js

@@ -90,10 +90,10 @@ fetch('./config.json')
     prompting and authenticate the user with the saved pat right away */
     .then(() => {
         if (localStorage.getItem("personalAccessToken") != null) {
-            personalAccessToken.value = localStorage.getItem("personalAccessToken")
+            console.log("personal access token found in local storage");
+            personalAccessToken.value = localStorage.getItem("personalAccessToken");
             patArea.hidden = true;
             authenticationButtonClicked();
-            console.log("personal access token found in local storage")
         }
     })
     .catch((err) => window.alert(`error initializing annotation editor: ${err}`))
@@ -235,7 +235,9 @@ async function getBranchFiles() {
     and directly get file content */
     if (fileName) { getFileContent() };
     try {
-        branch = branchSelect.value
+        if (!branch) {
+            branch = branchSelect.value;
+        };
         const response = await octokit.rest.repos.getContent({
             owner: repoOwner,
             repo: repoName,

### 2024-09-24 index.js
improve display of message & add paper

@@ -16,8 +16,6 @@ let commitConfirmButton = document.getElementById('commitConfirmButton');
 let bratArea = document.getElementById('bratArea');
 let showDocButton = document.getElementById('showDocButton');
 let commitMessage = document.getElementById('commitMessage');
-let filePathArea = document.getElementById('filePathArea');
-let filePathInfo = document.getElementById('filePathInfo');
 let message = document.getElementById('message');
 
 // initialize variables
@@ -51,7 +49,6 @@ branchSelectArea.hidden = true;
 fileSelectArea.hidden = true;
 commitArea.hidden = true;
 showDocButton.hidden = true;
-filePathArea.hidden = true;
 
 // attach event listener to buttons
 authenticationButton.addEventListener('click', authenticationButtonClicked);
@@ -144,10 +141,24 @@ function loadJson(data) {
 
 // use the dispatcher to update the content to display in Brat editor
 function updateBratEditor() {
-    if (brat) {
-        brat.dispatcher.post('requestRenderData', [docData]);
-        brat.dispatcher.post('current', [collData, docData, {}]);
+    try {
+        if (brat) {
+            brat.dispatcher.post('requestRenderData', [docData]);
+            brat.dispatcher.post('current', [collData, docData, {}]);
+        }
+
+        // Display successful message for 5 seconds
+        message.innerHTML = `Sucessfully loaded file content:<br/>${repoName}/${fileName}, branch ${branch}`;
+        setTimeout(function () {
+            message.innerHTML = '';
+        }, 5000);
     }
+    catch (error) {
+        window.alert(`Error updating Brat editor\n
+            error message: ${error}
+            `)
+    }
+
 }
 
 /* retrieve all existing branches of the given repository
@@ -294,8 +305,6 @@ async function getFileContent() {
             `)
     }
     commitArea.hidden = false;
-    filePathArea.hidden = false;
-    filePathInfo.value = repoName + "/" + fileName + `\nbranch ${branch}`
 }
 
 // function to check if a string is in json format
@@ -311,6 +320,20 @@ const extractJSON = (str) => {
 // commit the annotations and push to repository
 async function pushCommit() {
     try {
+        /* prepare for the commit */
+
+        // if current file is not json file, create a new json file with same name
+        if (fileName.length > 0) {
+            if (!fileName.includes(".json")) {
+                fileName = fileName.replace(/\..+/i, ".json")
+            }
+        } else {
+            fileName = "newFile.json"
+        }
+
+        // display message
[…]

### 2024-09-25 paper/main.tex
improve display of message & add paper
hide commit area in start & update paper

@@
 % This is used in the PDF meta data
-\title{SBAT: A Simple Browser-based Annotation Tool with Interactive Visualization and Github Support}
+\title{SBAT: A Simple Browser-based Annotation Tool with Interactive Visualization and GitHub Support}
 \author{Jia Sheng}
@@
 {\bfseries\LARGE
-SBAT: A Simple Browser-Based Annotation Tool with Interative Visualization and Github Support
+SBAT: A Simple Browser-Based Annotation Tool with Interative Visualization and GitHub Support
 }\\[1cm]
@@
 %% Uncomment once you want to add the anti-plagiarism statement file
-% \newpage
-% \includepdf[pages=-]{name-of-anti-plagiarism-statement-file}
+%\newpage
+%\includepdf[pages=-]{antiplagarism.pdf}
 \newpage
@@
 In computational linguistics, annotating linguistic data is a crucial step for many studies, and many tools can be used to facilitate the creation of annotated data.
-This paper introduces SBAT, a lightweight and easy-to-use web annotation tool.
+This thesis introduces SBAT, a lightweight and easy-to-use annotation tool.
 It supports annotation tasks that require attaching labels to text spans, such as POS tagging or labeling for named entity recognition.
 Among the various applications previously developed for the purpose of text annotation, many require a dedicated server or a local installation, which complicates the usage.
-On the contrary, SBAT is designed to be an online annotation tool that is easy to access and simple to use.
-It is built on the Brat annotation interface, but is completely browser-based and server-free, while preserving most of the key functionalities.
-Additionally, it provides support for integration with Github's file management system, which facilitates version control and user management in annotation projects.
+On the contrary, SBAT is designed to be a browser-based annotation tool that is easy to access and simple to use.
+It is built on the BRAT annotation editor, but is completely server-free, while preserving most of the key functionalities.
+Additionally, it provides support for integration with GitHub's file management system, which facilitates version control and user management in annotation projects.
 \newpage
@@
 \section{Introduction}
-Annotated data serves as the foundation for many linguistic studies, based on which it is possible to examine patterns, study linguistic phenomena, train statistical models or testify linguistic theories.
+Annotated data serves as the foundation for many linguistic studies, based on which it is possible to examine patterns, study linguistic phenomena, train statistical models or test linguistic theories.
 And among all types of data, text annotation is the most prevalent.
@@
 \\
-The rest of this paper is therefore divided into four sections, all dedicated to the introduction of SBAT and its comparison with the current popular annotation tools.
+The rest of this thesis is therefore divided into four sections, all dedicated to the introduction of SBAT and its comparison with the current popular annotation tools.
 The second chapter deals with the relevant works in the field, presenting a few representative annotation tools developed over the years, along with an overview of their functionalities, advantages and limitations.
@@
 Following that, the fourth chapter talks about the technical details of implementation in the development of SBAT.
-Finally, this paper ends with concluding remarks about SBAT, illustrating its strengths and limitations.
+Finally, this thesis ends with concluding remarks about SBAT, illustrating its strengths and limitations.
 
@@
 It is implemented using HTML and JavaScript, and can be used to attach user-defined labels to whole texts.
-It also allows the local import and export of annotation files.
-Building on that, the current version addresses the limitations of the previous one by enabling functionalities such as span annotations, editor UI, visualization, and Github support.
+It also allows to import JSON or txt files from the local device or export annotations in a JSON file.
+Building on that, the current version addresses the limitations of the previous one by enabling functionalities such as span annotations, editor UI, visualization, and GitHub support.\\
 \newpage
@@
 \\
-To create a new annotation, one can simply double-click or drag to select a span of characters with his mouse.
+When SBAT is started in the browser for the first time, an interactive editor with the default example file as well as the user authentication slot will be displayed.
+The editor view can be utilized by new users to experiment with the annotation operations and configurations without the need to log in.
+If the user has already logged in previously using the same browser, however, the log-in step will be skipped.
+Then, depending on whether the information about file paths has been provided in the config file, the user might be directly redirected to the editing page of an annotation file or will be prompted to select the file from a drop-down list.
+All those steps are guided with clear instructions in the user interface.\\
+\\
+In the editor, to create a new annotation, one can simply double-click or drag to select a span of characters with his mouse.
 A pop-up window will then appear [\hyperref[figure1]{Figure 1}], with a list of label options that the user has pre-defined in the config file.
@@
 The corresponding fragments will then share the same label, and can be moved or deleted.\\
-\\
-Besides the main annotation editor, there is also an area for GitHub authentication as well as for the import and export of annotation files.
-Depending on whether the user has previously successfully logged in using the current browser and whether the information about file paths has been provided in the config file, the user might be directly redirected to the editing page of an annotation file or will be prompted to provide authentication token and to select the file from a drop-down list [\hyperref[figure3]{Figure 3}].
-All those steps will be guided with clear instructions in the user interface.
+
 \begin{figure}[H]
@@
 }
-{\setstretch{1.0}\scriptsize This pop-up window appears when double-clicking or dragging to select a span of text in the editor.
+{\setstretch{1.0} This pop-up window appears when double-clicking or dragging to select a span of text in the editor.
 The displayed options are defined in the config file, in this case two entity types, "Person" and "Object".\par}
 \end{figure}
-\subsection{Github Support}
-SBAT enables users to import files from or export annotations to the GitHub repositories to which they have access.
-To do so, one only has to enter his Github Personal Access Token, and can then select the branch and the filename -- if not already provided in the config file -- to open the file in the annotation editor.
-To export annotations, the user can optionally enter a commit message in the input field and then click the "commit" button.
-In the whole process, if any error occurs in any step, the user will be prompted with the error message with hints to fix it, or, in terms of successful commit, also a message that indicates success.
-By making use of GitHub commits, the versions of annotations can be well documented and managed.\\
+\subsection{GitHub Support}
+SBAT enables users to import files from or export annotations to the GitHub repositories to which they have access, which means both the text content to be annotated as well as the annotations can be stored on GitHub to track or restore any changes.
+By incorporating those functionalities, one can not only conveniently document the versions of annotations, but also efficiently manage the tasks of members in a larger annotation project.\\
+\\
+To make use of these functions, one needs to first pass a user authentication, which is done by entering his GitHub Personal Access Token in the SBAT user interface.
+After successful authentication, the user will be prompted to select the branch and the filename -- if not already provided in the config file -- to open the selected file in SBAT.
+Once completed, the authentication or file selection area will be hidden, the commit button as well as a temporary notification indicating the successful loading of the file from the given path will appear in the user interface, and the chosen file will be displayed in the editor ready for annotating.\\
 \\
@@
 }
-{\setstretch{1.0}\scriptsize Annotations can be exported into a JSON file, and when loading this file in SBAT, all previous annotations will be visualized in the editor.\par}
+{\setstretch{1.0} Annotations can be exported into a JSON file, and when loading this file in SBAT, all previous annotations will be visualized in the editor.\par}
 \end{figure}
 
-For file exports, after the user hits the commit button, a JSON file with the original text and its annotation metadata will be committed to the same GitHub repository from which the file was originally imported.
+Once the user successfully loads a file from GitHub in the SBAT editor, the exportation of annotations is also straightforward.
+For that purpose, the user can optionally leave a commit message to document his changes in the input field, and then click the "commit" button.
+As a result, a JSON file with the original text and its annotation metadata will be committed to the same GitHub repository from which the file was originally imported.
+If the previously imported file is already a JSON file, this operation will overwrite the previous file.
+Otherwise, a new JSON file with the same file name will be created and appended to the repository.
 One example of such SBAT-generated JSON files can be found in the "example data" folder.
 The JSON format not only enables the visualization of those annotations in SBAT, but also facilitates programmatic parsing for future purposes.\\
+\\
+In any step of interacting with GitHub's repository system, if an error occurs, the user will be prompted with the error message with hints to fix it, or, in terms of successful commit, also a message that indicates success.
+In most cases, it is recommended to check the validity of the Personal Access Token as well as the repository name, owner, branch and file path entered in the config file.
+The user account also needs to have or be granted access to the source of the content on GitHub.\\
 \\
@@
 But unlike Brat, all logics of SBAT are executed in the browser, so there is no need for software installation or server configuration.
-Furthermore, SBAT makes use of the localStorage of the browser to save the user's Personal Access Token once logged in, and automatically logs the user in the next time when the site is started in the same browser.
-This is to simplify the log-in process and to allow users to concentrate on real annotation tasks.
-If one then wishes to log in with a different token, he can utilize the "clear history" function of the browser to clear the previously saved token.
-Due to its simple construction, it is fast to start and convenient to adapt for different purposes.
+This is to avoid dependencies on external software or devices.
+As almost all modern computers or mobile devices are equipped with a browser, its accessibility for all users is ensured at a low cost.
+Moreover, due to its simple construction, it is fast to start and convenient to adapt for different purposes.\\
+\\
+Since SBAT functions in the browser, it is able to utilize the localStorage of the browser to save the user's Personal Access Token once logged in, and automatically logs the user in the next time when the site is started in the same browser.
+That design intends to simplify the log-in process and allow users to concentrate on real annotation tasks.
+If one wishes to log in with a different account, however, he can utilize the "clear history" function of the browser to clear the previously saved token.
+By doing so, the authentication page will be shown when restarting SBAT, allowing a new token to be entered.
 
 \subsection{Flexible Configuration}
-Configuration of SBAT is allowed in the config.json file, which makes it easy for users to customize and tailor it to different tasks.
+Configuration of SBAT is allowed in the config.json file, which is located in the root folder of SBAT.
+The config file allows centralized management of all annotation-project-related configurations, for instance, the definition of annotation labels and file locations.
+It aims to simplify user customisation and entitle SBAT to be tailored to a variety of annotation tasks.\\
+\\
 For importing files from GitHub, the user is able to enter the repository name, owner, branch and file path under the "admin config" attribute in advance, which will allow SBAT to skip the intermediate file selection process in every start [\hyperref[figure3]{Figure 3}] and to directly display the pre-defined file in the annotation editor.
@@
 }
-{\setstretch{1.0}\scriptsize The "branch" and "filePath" attributes in "admin config" are optional.
-If no value is provided, SBAT will prompt the user with a drop-down list with available branch or file names to select from.\par}
+{\setstretch{1.0} 
+The "branch" and "filePath" attributes in "admin config" are optional. If no value is provided, SBAT will prompt the user with a drop-down list with available branch or file names to select from.
+\par}
 \end{figure}
@@
 \subsection{Annotation UI}
-SBAT's annotation editor is rooted in the frontend component from Brat, which is implemented using XHTML, Scalable Vector Graphics (SVG), JavaScript, and jQuery.
-On top of that, to remove Brat's server-side dependence, the user operations in the editor, such as creating, editing or deleting annotations, are all handled by the browser.
+SBAT's annotation editor is rooted in the frontend component from BRAT, which is implemented using XHTML, Scalable Vector Graphics (SVG), JavaScript, and jQuery.
+In more detail, in order to replicate the annotation editor, the HTML -- including the SVG graphics -- of the BRAT editor and pop-up windows is included in the user interface of SBAT.
+Besides, to enable the interactivity of editor components, the JavaScript scripts from the BRAT editor, including the annotator and visualizer modules, are converted into ECMAScript modules and implemented in SBAT.
+Two CSS files are imported as well to add style to those HTML components.
+As the editor component is more time-consuming and requires data from other parts, it is always the last to load in a fresh start.
+That is to say, it will only be initialized in a JavaScript function after the DOM tree of the HTML file is constructed and the config file is successfully loaded.
+\\
+\\
+On top of that, to remove BRAT's server-side dependence, the user operations in the editor, such as creating, editing or deleting annotations, are all handled by the browser.
 This is realized by the LocalAjax class, adapting the LocalAjax function from brat-frontend-editor, which locally simulates AJAX requests to process the data without actually sending real network requests.
+As a result, whenever a new event is triggered by the user operation, it is handled by the functions to change the annotation value that is temporarily stored in the memory of the browser.
+And after that, the new value is sent to the editor component to update the displayed content as well.\\
+\\
 Other UI functions, such as user authentication, and import and export functions, are also implemented natively in JavaScript.
-In this way, all functionalities of the user interface are realized in the script files attached to an HTML webpage and are locally executed by the browser.
+And so forth, all functionalities of the user interface are realized in the script files attached to an HTML webpage and are locally executed in the browser.
 \subsection{Browser-Based Construction}
 As SBAT is a static web app without server communications, it can be hosted on GitHub Pages for free.
-It is not mandatory, though, to host the app on the internet in order to use it, as the index.html file can be used as an entry point to start the app locally in the browser.
-Nonetheless, if the user plans to access it on the web instead of locally, he can directly upload SBAT's source code to his Github repository to host a copy on his Github Pages.
+It is not mandatory, though, to host the app on the Internet in order to use it, as the index.html file can be used as an entry point to start the app locally in the browser.
+Nonetheless, if the user plans to access it on the web instead of locally, he can directly upload SBAT's source code to his GitHub repository to host a copy on his GitHub Pages.
 For the development stage, a copy of SBAT is also hosted on the GitHub Pages, which is done by heading to the SBAT code repository on GitHub -> Settings -> Pages and selecting the option of deploying from the "main" branch.\\
@@
 This allows direct modification of each individual component without the need for re-bundling.
-\subsection{Usage of Github API}
-SBAT uses Octokit \footnote{https://esm.sh/octokit@2.1.0, last accessed on September 20th, 2024}, the official SDKs for the GitHub API, which enables to implement Github operations programmatically.
+\subsection{Usage of GitHub API}
+SBAT uses Octokit,\footnote{https://esm.sh/octokit@2.1.0, last accessed on September 20th, 2024} the official SDKs for the GitHub API, which enables to implement GitHub operations programmatically.
 The authentication through a user-provided GitHub Personal Access Token creates a new user-authenticated Octokit object, which can be used to obtain data from GitHub repositories to which the authenticated user has access.
@@
 \\
-During development, a test Github Personal Access Token is generated under GitHub -> Settings -> Developer Settings -> Personal access tokens.
+During development, a test GitHub Personal Access Token is generated under GitHub -> Settings -> Developer Settings -> Personal access tokens.
 SBAT only performs the absolutely necessary operations for file access and version control with GitHub authentication, namely retrieving lists of branches and file names under a specified repository, obtaining file content, getting information about the last commit, and creating new commits, so the scope of the Personal Access Token generated for SBAT only needs to cover those basic repository operations under the "Full control of private repositories" section.
@@
 To address those limitations, SBAT aims to provide a simpler and no-server solution for annotation projects.
-It retains the essential features of BRAT's annotation editor, such as annotation operations and visualizations, while offering integration with Github, enabling the import and export of annotations from and to user-authenticated Github repositories.
+It retains the essential features of BRAT's annotation editor, such as annotation operations and visualizations, while offering integration with GitHub, enabling the import and export of annotations from and to user-authenticated GitHub repositories.
 Although its usage is currently limited to text span annotation, it can be easily adapted or extended to accommodate the needs of different annotation tasks due to its modular structure and flexible configuration.\\

### 2024-09-25 index.js

@@ -11,7 +11,6 @@ let branchSelect = document.getElementById('branchSelect');
 let branchSelectButton = document.getElementById('branchSelectButton');
 let fileSelect = document.getElementById('fileSelect');
 let fileSelectButton = document.getElementById('fileSelectButton');
-let commitArea = document.getElementById('commitArea');
 let commitConfirmButton = document.getElementById('commitConfirmButton');
 let bratArea = document.getElementById('bratArea');
 let showDocButton = document.getElementById('showDocButton');
@@ -44,11 +43,12 @@ let docData = {
     [261, 267], [268, 271], [272, 274], [275, 284], [285, 287], [288, 300]]
 }
 
-// hide unwanted areas in the beginning
+// hide in the start elements which will needed later 
 branchSelectArea.hidden = true;
 fileSelectArea.hidden = true;
-commitArea.hidden = true;
 showDocButton.hidden = true;
+commitMessage.hidden = true;
+commitConfirmButton.hidden = true;
 
 // attach event listener to buttons
 authenticationButton.addEventListener('click', authenticationButtonClicked);
@@ -294,6 +294,8 @@ async function getFileContent() {
         }
         fileSelectArea.hidden = true;
         bratArea.hidden = false;
+        commitMessage.hidden = false;
+        commitConfirmButton.hidden = false;
     } catch (error) {
         window.alert(`Error fetching file content, please check if the following information is correct:\n
             repository owner: ${repoOwner}\n
@@ -304,7 +306,6 @@ async function getFileContent() {
             Note: Please also check if you have permission to access the file or if your Personal Access Token is still valid
             `)
     }
-    commitArea.hidden = false;
 }
 
 // function to check if a string is in json format
@@ -332,7 +333,7 @@ async function pushCommit() {
         }
 
         // display message
-        message.innerHTML = `Commiting ${repoName}/${fileName},  branch ${branch}<br/>Please wait :)`;
+        message.innerHTML = `Committing ${repoName}/${fileName},  branch ${branch}<br/>Please wait :)`;
 
         /* retrieve previous commit */
 
